\SpecialChapter{Summary of Forms}

\label{summary_h0}




The table that follows summarizes the Scheme syntactic forms and
procedures described in Chapters \ref{binding_g88} through \ref{exceptions_g147}.
It shows the category of the form and the page number where it
is defined.
The category states whether the form describes a syntactic form or
a procedure.


All page numbers appearing here refer to the printed version of this
book and also serve as hypertext links to the corresponding locations
in the electronic version of this book.

\begin{longtabu} to \textwidth {Llr}\toprule
Form & Category & Page \\\midrule\endhead
\midrule{}See next page & & \\\bottomrule\endfoot
\midrule{}End & & \\\bottomrule\endlastfoot
\texttt{'\textit{obj}} & syntax & \pageref{objects_s2} \\
\texttt{`\textit{obj}} & syntax & \pageref{objects_s5} \\
\texttt{,\textit{obj}} & syntax & \pageref{objects_s5} \\
\texttt{,\@{}\textit{obj}} & syntax & \pageref{objects_s5} \\
\texttt{=\textgreater{}} & syntax & \pageref{control_s16} \\
\texttt{\_{}} & syntax & \pageref{syntax_s26} \\
\texttt{...} & syntax & \pageref{syntax_s26} \\
\texttt{\#{}'\textit{template}} & syntax & \pageref{syntax_s33} \\
\texttt{\#{}`\textit{template}} & syntax & \pageref{syntax_s40} \\
\texttt{\#{},\textit{template}} & syntax & \pageref{syntax_s40} \\
\texttt{\#{},\@{}\textit{template}} & syntax & \pageref{syntax_s40} \\
\texttt{\&{}assertion} & syntax & \pageref{exceptions_s21} \\
\texttt{\&{}condition} & syntax & \pageref{exceptions_s13} \\
\texttt{\&{}error} & syntax & \pageref{exceptions_s22} \\
\texttt{\&{}i/o} & syntax & \pageref{exceptions_s32} \\
\texttt{\&{}i/o-decoding} & syntax & \pageref{exceptions_s42} \\
\texttt{\&{}i/o-encoding} & syntax & \pageref{exceptions_s43} \\
\texttt{\&{}i/o-file-already-exists} & syntax & \pageref{exceptions_s39} \\
\texttt{\&{}i/o-file-does-not-exist} & syntax & \pageref{exceptions_s40} \\
\texttt{\&{}i/o-file-is-read-only} & syntax & \pageref{exceptions_s38} \\
\texttt{\&{}i/o-file-protection} & syntax & \pageref{exceptions_s37} \\
\texttt{\&{}i/o-filename} & syntax & \pageref{exceptions_s36} \\
\texttt{\&{}i/o-invalid-position} & syntax & \pageref{exceptions_s35} \\
\texttt{\&{}i/o-port} & syntax & \pageref{exceptions_s41} \\
\texttt{\&{}i/o-read} & syntax & \pageref{exceptions_s33} \\
\texttt{\&{}i/o-write} & syntax & \pageref{exceptions_s34} \\
\texttt{\&{}implementation-restriction} & syntax & \pageref{exceptions_s28} \\
\texttt{\&{}irritants} & syntax & \pageref{exceptions_s25} \\
\texttt{\&{}lexical} & syntax & \pageref{exceptions_s29} \\
\texttt{\&{}message} & syntax & \pageref{exceptions_s24} \\
\texttt{\&{}no-infinities} & syntax & \pageref{exceptions_s44} \\
\texttt{\&{}no-nans} & syntax & \pageref{exceptions_s45} \\
\texttt{\&{}non-continuable} & syntax & \pageref{exceptions_s27} \\
\texttt{\&{}serious} & syntax & \pageref{exceptions_s19} \\
\texttt{\&{}syntax} & syntax & \pageref{exceptions_s30} \\
\texttt{\&{}undefined} & syntax & \pageref{exceptions_s31} \\
\texttt{\&{}violation} & syntax & \pageref{exceptions_s20} \\
\texttt{\&{}warning} & syntax & \pageref{exceptions_s23} \\
\texttt{\&{}who} & syntax & \pageref{exceptions_s26} \\
\texttt{(* \textit{num} ...)} & procedure & \pageref{objects_s91} \\
\texttt{(+ \textit{num} ...)} & procedure & \pageref{objects_s89} \\
\texttt{(- \textit{num})} & procedure & \pageref{objects_s90} \\
\texttt{(- \textit{num\textsubscript{1}} \textit{num\textsubscript{2}} \textit{num\textsubscript{3}} ...)} & procedure & \pageref{objects_s90} \\
\texttt{(/ \textit{num})} & procedure & \pageref{objects_s92} \\
\texttt{(/ \textit{num\textsubscript{1}} \textit{num\textsubscript{2}} \textit{num\textsubscript{3}} ...)} & procedure & \pageref{objects_s92} \\
\texttt{(\textless{} \textit{real\textsubscript{1}} \textit{real\textsubscript{2}} \textit{real\textsubscript{3}} ...)} & procedure & \pageref{objects_s88} \\
\texttt{(\textless{}= \textit{real\textsubscript{1}} \textit{real\textsubscript{2}} \textit{real\textsubscript{3}} ...)} & procedure & \pageref{objects_s88} \\
\texttt{(= \textit{num\textsubscript{1}} \textit{num\textsubscript{2}} \textit{num\textsubscript{3}} ...)} & procedure & \pageref{objects_s88} \\
\texttt{(\textgreater{} \textit{real\textsubscript{1}} \textit{real\textsubscript{2}} \textit{real\textsubscript{3}} ...)} & procedure & \pageref{objects_s88} \\
\texttt{(\textgreater{}= \textit{real\textsubscript{1}} \textit{real\textsubscript{2}} \textit{real\textsubscript{3}} ...)} & procedure & \pageref{objects_s88} \\
\texttt{(abs \textit{real})} & procedure & \pageref{objects_s105} \\
\texttt{(acos \textit{num})} & procedure & \pageref{objects_s132} \\
\texttt{(and \textit{expr} ...)} & syntax & \pageref{control_s11} \\
\texttt{(angle \textit{num})} & procedure & \pageref{objects_s124} \\
\texttt{(append)} & procedure & \pageref{objects_s49} \\
\texttt{(append \textit{list} ... \textit{obj})} & procedure & \pageref{objects_s49} \\
\texttt{(apply \textit{procedure} \textit{obj} ... \textit{list})} & procedure & \pageref{control_s3} \\
\texttt{(asin \textit{num})} & procedure & \pageref{objects_s132} \\
\texttt{(assert \textit{expression})} & syntax & \pageref{exceptions_s5} \\
\texttt{(assertion-violation \textit{who} \textit{msg} \textit{irritant} ...)} & procedure & \pageref{exceptions_s4} \\
\texttt{(assertion-violation? \textit{obj})} & procedure & \pageref{exceptions_s21} \\
\texttt{(assoc \textit{obj} \textit{alist})} & procedure & \pageref{objects_s58} \\
\texttt{(assp \textit{procedure} \textit{alist})} & procedure & \pageref{objects_s60} \\
\texttt{(assq \textit{obj} \textit{alist})} & procedure & \pageref{objects_s58} \\
\texttt{(assv \textit{obj} \textit{alist})} & procedure & \pageref{objects_s58} \\
\texttt{(atan \textit{num})} & procedure & \pageref{objects_s133} \\
\texttt{(atan \textit{real\textsubscript{1}} \textit{real\textsubscript{2}})} & procedure & \pageref{objects_s133} \\
\texttt{(begin \textit{expr\textsubscript{1}} \textit{expr\textsubscript{2}} ...)} & syntax & \pageref{control_s4} \\
\texttt{(binary-port? \textit{obj})} & procedure & \pageref{io_s45} \\
\texttt{(bitwise-and \textit{exint} ...)} & procedure & \pageref{objects_s134} \\
\texttt{(bitwise-arithmetic-shift \textit{exint\textsubscript{1}} \textit{exint\textsubscript{2}})} & procedure & \pageref{objects_s144} \\
\texttt{(bitwise-arithmetic-shift-left \textit{exint\textsubscript{1}} \textit{exint\textsubscript{2}})} & procedure & \pageref{objects_s143} \\
\texttt{(bitwise-arithmetic-shift-right \textit{exint\textsubscript{1}} \textit{exint\textsubscript{2}})} & procedure & \pageref{objects_s143} \\
\texttt{(bitwise-bit-count \textit{exint})} & procedure & \pageref{objects_s136} \\
\texttt{(bitwise-bit-field \textit{exint\textsubscript{1}} \textit{exint\textsubscript{2}} \textit{exint\textsubscript{3}})} & procedure & \pageref{objects_s141} \\
\texttt{(bitwise-bit-set? \textit{exint\textsubscript{1}} \textit{exint\textsubscript{2}})} & procedure & \pageref{objects_s139} \\
\texttt{(bitwise-copy-bit \textit{exint\textsubscript{1}} \textit{exint\textsubscript{2}} \textit{exint\textsubscript{3}})} & procedure & \pageref{objects_s140} \\
\texttt{(bitwise-copy-bit-field \textit{exint\textsubscript{1}} \textit{exint\textsubscript{2}} \textit{exint\textsubscript{3}}\allowbreak \textit{exint\textsubscript{4}})} & procedure & \pageref{objects_s142} \\
\texttt{(bitwise-first-bit-set \textit{exint})} & procedure & \pageref{objects_s138} \\
\texttt{(bitwise-if \textit{exint\textsubscript{1}} \textit{exint\textsubscript{2}} \textit{exint\textsubscript{3}})} & procedure & \pageref{objects_s135} \\
\texttt{(bitwise-ior \textit{exint} ...)} & procedure & \pageref{objects_s134} \\
\texttt{(bitwise-length \textit{exint})} & procedure & \pageref{objects_s137} \\
\texttt{(bitwise-not \textit{exint})} & procedure & \pageref{objects_s134} \\
\texttt{(bitwise-reverse-bit-field \textit{exint\textsubscript{1}} \textit{exint\textsubscript{2}} \textit{exint\textsubscript{3}})} & procedure & \pageref{objects_s146} \\
\texttt{(bitwise-rotate-bit-field \textit{exint\textsubscript{1}} \textit{exint\textsubscript{2}} \textit{exint\textsubscript{3}}\allowbreak \textit{exint\textsubscript{4}})} & procedure & \pageref{objects_s145} \\
\texttt{(bitwise-xor \textit{exint} ...)} & procedure & \pageref{objects_s134} \\
\texttt{(boolean=? \textit{boolean\textsubscript{1}} \textit{boolean\textsubscript{2}})} & procedure & \pageref{objects_s271} \\
\texttt{(boolean? \textit{obj})} & procedure & \pageref{objects_s14} \\
\texttt{(bound-identifier=? \textit{identifier\textsubscript{1}} \textit{identifier\textsubscript{2}})} & procedure & \pageref{syntax_s37} \\
\texttt{(buffer-mode \textit{symbol})} & syntax & \pageref{io_s27} \\
\texttt{(buffer-mode? \textit{obj})} & syntax & \pageref{io_s28} \\
\texttt{(bytevector-\textgreater{}sint-list \textit{bytevector} \textit{eness} \textit{size})} & procedure & \pageref{objects_s260} \\
\texttt{(bytevector-\textgreater{}string \textit{bytevector} \textit{transcoder})} & procedure & \pageref{io_s91} \\
\texttt{(bytevector-\textgreater{}u8-list \textit{bytevector})} & procedure & \pageref{objects_s252} \\
\texttt{(bytevector-\textgreater{}uint-list \textit{bytevector} \textit{eness} \textit{size})} & procedure & \pageref{objects_s260} \\
\texttt{(bytevector-copy \textit{bytevector})} & procedure & \pageref{objects_s246} \\
\texttt{(bytevector-copy! \textit{src} \textit{src-start}\allowbreak \textit{dst} \textit{dst-start} \textit{n})} & procedure & \pageref{objects_s247} \\
\texttt{(bytevector-fill! \textit{bytevector} \textit{fill})} & procedure & \pageref{objects_s245} \\
\texttt{(bytevector-ieee-double-native-ref\allowbreak \textit{bytevector} \textit{n})} & procedure & \pageref{objects_s262} \\
\texttt{(bytevector-ieee-double-native-set!\allowbreak \textit{bytevector} \textit{n} \textit{x})} & procedure & \pageref{objects_s263} \\
\texttt{(bytevector-ieee-double-ref \textit{bytevector} \textit{n} \textit{eness})} & procedure & \pageref{objects_s264} \\
\texttt{(bytevector-ieee-double-set! \textit{bytevector} \textit{n} \textit{x} \textit{eness})} & procedure & \pageref{objects_s265} \\
\texttt{(bytevector-ieee-single-native-ref \textit{bytevector} \textit{n})} & procedure & \pageref{objects_s262} \\
\texttt{(bytevector-ieee-single-native-set! \textit{bytevector} \textit{n} \textit{x})} & procedure & \pageref{objects_s263} \\
\texttt{(bytevector-ieee-single-ref \textit{bytevector} \textit{n} \textit{eness})} & procedure & \pageref{objects_s264} \\
\texttt{(bytevector-ieee-single-set! \textit{bytevector} \textit{n} \textit{x} \textit{eness})} & procedure & \pageref{objects_s265} \\
\texttt{(bytevector-length \textit{bytevector})} & procedure & \pageref{objects_s243} \\
\texttt{(bytevector-s16-native-ref \textit{bytevector} \textit{n})} & procedure & \pageref{objects_s254} \\
\texttt{(bytevector-s16-native-set! \textit{bytevector} \textit{n} \textit{s16})} & procedure & \pageref{objects_s255} \\
\texttt{(bytevector-s16-ref \textit{bytevector} \textit{n} \textit{eness})} & procedure & \pageref{objects_s256} \\
\texttt{(bytevector-s16-set! \textit{bytevector} \textit{n} \textit{s16} \textit{eness})} & procedure & \pageref{objects_s257} \\
\texttt{(bytevector-s32-native-ref \textit{bytevector} \textit{n})} & procedure & \pageref{objects_s254} \\
\texttt{(bytevector-s32-native-set! \textit{bytevector} \textit{n} \textit{s32})} & procedure & \pageref{objects_s255} \\
\texttt{(bytevector-s32-ref \textit{bytevector} \textit{n} \textit{eness})} & procedure & \pageref{objects_s256} \\
\texttt{(bytevector-s32-set! \textit{bytevector} \textit{n} \textit{s32} \textit{eness})} & procedure & \pageref{objects_s257} \\
\texttt{(bytevector-s64-native-ref \textit{bytevector} \textit{n})} & procedure & \pageref{objects_s254} \\
\texttt{(bytevector-s64-native-set! \textit{bytevector} \textit{n} \textit{s64})} & procedure & \pageref{objects_s255} \\
\texttt{(bytevector-s64-ref \textit{bytevector} \textit{n} \textit{eness})} & procedure & \pageref{objects_s256} \\
\texttt{(bytevector-s64-set! \textit{bytevector} \textit{n} \textit{s64} \textit{eness})} & procedure & \pageref{objects_s257} \\
\texttt{(bytevector-s8-ref \textit{bytevector} \textit{n})} & procedure & \pageref{objects_s249} \\
\texttt{(bytevector-s8-set! \textit{bytevector} \textit{n} \textit{s8})} & procedure & \pageref{objects_s251} \\
\texttt{(bytevector-sint-ref \textit{bytevector} \textit{n} \textit{eness} \textit{size})} & procedure & \pageref{objects_s258} \\
\texttt{(bytevector-sint-set! \textit{bytevector} \textit{n} \textit{sint} \textit{eness} \textit{size})} & procedure & \pageref{objects_s259} \\
\texttt{(bytevector-u16-native-ref \textit{bytevector} \textit{n})} & procedure & \pageref{objects_s254} \\
\texttt{(bytevector-u16-native-set! \textit{bytevector} \textit{n} \textit{u16})} & procedure & \pageref{objects_s255} \\
\texttt{(bytevector-u16-ref \textit{bytevector} \textit{n} \textit{eness})} & procedure & \pageref{objects_s256} \\
\texttt{(bytevector-u16-set! \textit{bytevector} \textit{n} \textit{u16} \textit{eness})} & procedure & \pageref{objects_s257} \\
\texttt{(bytevector-u32-native-ref \textit{bytevector} \textit{n})} & procedure & \pageref{objects_s254} \\
\texttt{(bytevector-u32-native-set! \textit{bytevector} \textit{n} \textit{u32})} & procedure & \pageref{objects_s255} \\
\texttt{(bytevector-u32-ref \textit{bytevector} \textit{n} \textit{eness})} & procedure & \pageref{objects_s256} \\
\texttt{(bytevector-u32-set! \textit{bytevector} \textit{n} \textit{u32} \textit{eness})} & procedure & \pageref{objects_s257} \\
\texttt{(bytevector-u64-native-ref \textit{bytevector} \textit{n})} & procedure & \pageref{objects_s254} \\
\texttt{(bytevector-u64-native-set! \textit{bytevector} \textit{n} \textit{u64})} & procedure & \pageref{objects_s255} \\
\texttt{(bytevector-u64-ref \textit{bytevector} \textit{n} \textit{eness})} & procedure & \pageref{objects_s256} \\
\texttt{(bytevector-u64-set! \textit{bytevector} \textit{n} \textit{u64} \textit{eness})} & procedure & \pageref{objects_s257} \\
\texttt{(bytevector-u8-ref \textit{bytevector} \textit{n})} & procedure & \pageref{objects_s248} \\
\texttt{(bytevector-u8-set! \textit{bytevector} \textit{n} \textit{u8})} & procedure & \pageref{objects_s250} \\
\texttt{(bytevector-uint-ref \textit{bytevector} \textit{n} \textit{eness} \textit{size})} & procedure & \pageref{objects_s258} \\
\texttt{(bytevector-uint-set! \textit{bytevector} \textit{n} \textit{uint} \textit{eness} \textit{size})} & procedure & \pageref{objects_s259} \\
\texttt{(bytevector=? \textit{bytevector\textsubscript{1}} \textit{bytevector\textsubscript{2}})} & procedure & \pageref{objects_s244} \\
\texttt{(bytevector? \textit{obj})} & procedure & \pageref{objects_s24} \\
\texttt{(caaaar \textit{pair})} & procedure & \pageref{objects_s42} \\
\texttt{(caaadr \textit{pair})} & procedure & \pageref{objects_s42} \\
\texttt{(caaar \textit{pair})} & procedure & \pageref{objects_s42} \\
\texttt{(caadar \textit{pair})} & procedure & \pageref{objects_s42} \\
\texttt{(caaddr \textit{pair})} & procedure & \pageref{objects_s42} \\
\texttt{(caadr \textit{pair})} & procedure & \pageref{objects_s42} \\
\texttt{(caar \textit{pair})} & procedure & \pageref{objects_s42} \\
\texttt{(cadaar \textit{pair})} & procedure & \pageref{objects_s42} \\
\texttt{(cadadr \textit{pair})} & procedure & \pageref{objects_s42} \\
\texttt{(cadar \textit{pair})} & procedure & \pageref{objects_s42} \\
\texttt{(caddar \textit{pair})} & procedure & \pageref{objects_s42} \\
\texttt{(cadddr \textit{pair})} & procedure & \pageref{objects_s42} \\
\texttt{(caddr \textit{pair})} & procedure & \pageref{objects_s42} \\
\texttt{(cadr \textit{pair})} & procedure & \pageref{objects_s42} \\
\texttt{(call-with-bytevector-output-port \textit{procedure})} & procedure & \pageref{io_s38} \\
\texttt{(call-with-bytevector-output-port \textit{procedure} \textit{?transcoder})} & procedure & \pageref{io_s38} \\
\texttt{(call-with-current-continuation \textit{procedure})} & procedure & \pageref{control_s54} \\
\texttt{(call-with-input-file \textit{path} \textit{procedure})} & procedure & \pageref{io_s77} \\
\texttt{(call-with-output-file \textit{path} \textit{procedure})} & procedure & \pageref{io_s78} \\
\texttt{(call-with-port \textit{port} \textit{procedure})} & procedure & \pageref{io_s51} \\
\texttt{(call-with-string-output-port \textit{procedure})} & procedure & \pageref{io_s39} \\
\texttt{(call-with-values \textit{producer} \textit{consumer})} & procedure & \pageref{control_s71} \\
\texttt{(call/cc \textit{procedure})} & procedure & \pageref{control_s54} \\
\texttt{(car \textit{pair})} & procedure & \pageref{objects_s38} \\
\texttt{(case \textit{expr\textsubscript{0}} \textit{clause\textsubscript{1}} \textit{clause\textsubscript{2}} ...)} & syntax & \pageref{control_s18} \\
\texttt{(case-lambda \textit{clause} ...)} & syntax & \pageref{binding_s13} \\
\texttt{(cdaaar \textit{pair})} & procedure & \pageref{objects_s42} \\
\texttt{(cdaadr \textit{pair})} & procedure & \pageref{objects_s42} \\
\texttt{(cdaar \textit{pair})} & procedure & \pageref{objects_s42} \\
\texttt{(cdadar \textit{pair})} & procedure & \pageref{objects_s42} \\
\texttt{(cdaddr \textit{pair})} & procedure & \pageref{objects_s42} \\
\texttt{(cdadr \textit{pair})} & procedure & \pageref{objects_s42} \\
\texttt{(cdar \textit{pair})} & procedure & \pageref{objects_s42} \\
\texttt{(cddaar \textit{pair})} & procedure & \pageref{objects_s42} \\
\texttt{(cddadr \textit{pair})} & procedure & \pageref{objects_s42} \\
\texttt{(cddar \textit{pair})} & procedure & \pageref{objects_s42} \\
\texttt{(cdddar \textit{pair})} & procedure & \pageref{objects_s42} \\
\texttt{(cddddr \textit{pair})} & procedure & \pageref{objects_s42} \\
\texttt{(cdddr \textit{pair})} & procedure & \pageref{objects_s42} \\
\texttt{(cddr \textit{pair})} & procedure & \pageref{objects_s42} \\
\texttt{(cdr \textit{pair})} & procedure & \pageref{objects_s39} \\
\texttt{(ceiling \textit{real})} & procedure & \pageref{objects_s103} \\
\texttt{(char-\textgreater{}integer \textit{char})} & procedure & \pageref{objects_s210} \\
\texttt{(char-alphabetic? \textit{char})} & procedure & \pageref{objects_s203} \\
\texttt{(char-ci\textless{}=? \textit{char\textsubscript{1}} \textit{char\textsubscript{2}} \textit{char\textsubscript{3}} ...)} & procedure & \pageref{objects_s202} \\
\texttt{(char-ci\textless{}? \textit{char\textsubscript{1}} \textit{char\textsubscript{2}} \textit{char\textsubscript{3}} ...)} & procedure & \pageref{objects_s202} \\
\texttt{(char-ci=? \textit{char\textsubscript{1}} \textit{char\textsubscript{2}} \textit{char\textsubscript{3}} ...)} & procedure & \pageref{objects_s202} \\
\texttt{(char-ci\textgreater{}=? \textit{char\textsubscript{1}} \textit{char\textsubscript{2}} \textit{char\textsubscript{3}} ...)} & procedure & \pageref{objects_s202} \\
\texttt{(char-ci\textgreater{}? \textit{char\textsubscript{1}} \textit{char\textsubscript{2}} \textit{char\textsubscript{3}} ...)} & procedure & \pageref{objects_s202} \\
\texttt{(char-downcase \textit{char})} & procedure & \pageref{objects_s207} \\
\texttt{(char-foldcase \textit{char})} & procedure & \pageref{objects_s209} \\
\texttt{(char-general-category \textit{char})} & procedure & \pageref{objects_s205} \\
\texttt{(char-lower-case? \textit{char})} & procedure & \pageref{objects_s204} \\
\texttt{(char-numeric? \textit{char})} & procedure & \pageref{objects_s203} \\
\texttt{(char-title-case? \textit{char})} & procedure & \pageref{objects_s204} \\
\texttt{(char-titlecase \textit{char})} & procedure & \pageref{objects_s208} \\
\texttt{(char-upcase \textit{char})} & procedure & \pageref{objects_s206} \\
\texttt{(char-upper-case? \textit{char})} & procedure & \pageref{objects_s204} \\
\texttt{(char-whitespace? \textit{char})} & procedure & \pageref{objects_s203} \\
\texttt{(char\textless{}=? \textit{char\textsubscript{1}} \textit{char\textsubscript{2}} \textit{char\textsubscript{3}} ...)} & procedure & \pageref{objects_s201} \\
\texttt{(char\textless{}? \textit{char\textsubscript{1}} \textit{char\textsubscript{2}} \textit{char\textsubscript{3}} ...)} & procedure & \pageref{objects_s201} \\
\texttt{(char=? \textit{char\textsubscript{1}} \textit{char\textsubscript{2}} \textit{char\textsubscript{3}} ...)} & procedure & \pageref{objects_s201} \\
\texttt{(char\textgreater{}=? \textit{char\textsubscript{1}} \textit{char\textsubscript{2}} \textit{char\textsubscript{3}} ...)} & procedure & \pageref{objects_s201} \\
\texttt{(char\textgreater{}? \textit{char\textsubscript{1}} \textit{char\textsubscript{2}} \textit{char\textsubscript{3}} ...)} & procedure & \pageref{objects_s201} \\
\texttt{(char? \textit{obj})} & procedure & \pageref{objects_s19} \\
\texttt{(close-input-port \textit{input-port})} & procedure & \pageref{io_s88} \\
\texttt{(close-output-port \textit{output-port})} & procedure & \pageref{io_s88} \\
\texttt{(close-port \textit{port})} & procedure & \pageref{io_s46} \\
\texttt{(command-line)} & procedure & \pageref{libraries_s17} \\
\texttt{(complex? \textit{obj})} & procedure & \pageref{objects_s17} \\
\texttt{(cond \textit{clause\textsubscript{1}} \textit{clause\textsubscript{2}} ...)} & syntax & \pageref{control_s13} \\
\texttt{(condition \textit{condition} ...)} & procedure & \pageref{exceptions_s15} \\
\texttt{(condition-accessor \textit{rtd} \textit{procedure})} & procedure & \pageref{exceptions_s18} \\
\texttt{(condition-irritants \textit{condition})} & procedure & \pageref{exceptions_s25} \\
\texttt{(condition-message \textit{condition})} & procedure & \pageref{exceptions_s24} \\
\texttt{(condition-predicate \textit{rtd})} & procedure & \pageref{exceptions_s18} \\
\texttt{(condition-who \textit{condition})} & procedure & \pageref{exceptions_s26} \\
\texttt{(condition? \textit{obj})} & procedure & \pageref{exceptions_s14} \\
\texttt{(cons \textit{obj\textsubscript{1}} \textit{obj\textsubscript{2}})} & procedure & \pageref{objects_s37} \\
\texttt{(cons* \textit{obj} ... \textit{final-obj})} & procedure & \pageref{objects_s44} \\
\texttt{\textit{constant}} & syntax & \pageref{objects_s1} \\
\texttt{(cos \textit{num})} & procedure & \pageref{objects_s131} \\
\texttt{(current-error-port)} & procedure & \pageref{io_s32} \\
\texttt{(current-input-port)} & procedure & \pageref{io_s32} \\
\texttt{(current-output-port)} & procedure & \pageref{io_s32} \\
\texttt{(datum-\textgreater{}syntax \textit{template-identifier} \textit{obj})} & procedure & \pageref{syntax_s45} \\
\texttt{(define \textit{var} \textit{expr})} & syntax & \pageref{binding_s24} \\
\texttt{(define \textit{var})} & syntax & \pageref{binding_s24} \\
\texttt{(define (\textit{var\textsubscript{0}} \textit{var\textsubscript{1}} ...) \textit{body\textsubscript{1}} \textit{body\textsubscript{2}} ...)} & syntax & \pageref{binding_s24} \\
\texttt{(define (\textit{var\textsubscript{0}} . \textit{var\textsubscript{r}}) \textit{body\textsubscript{1}} \textit{body\textsubscript{2}} ...)} & syntax & \pageref{binding_s24} \\
\texttt{(define (\textit{var\textsubscript{0}} \textit{var\textsubscript{1}} \textit{var\textsubscript{2}} ... . \textit{var\textsubscript{r}}) \textit{body\textsubscript{1}} \textit{body\textsubscript{2}} ...)} & syntax & \pageref{binding_s24} \\
\texttt{(define-condition-type \textit{name} \textit{parent} \textit{constructor}\allowbreak \textit{pred} \textit{field} ...)} & syntax & \pageref{exceptions_s17} \\
\texttt{(define-enumeration \textit{name} (\textit{symbol} ...)\allowbreak \textit{constructor})} & syntax & \pageref{objects_s290} \\
\texttt{(define-record-type \textit{record-name} \textit{clause} ...)} & syntax & \pageref{records_s13} \\
\texttt{(define-record-type (\textit{record-name} \textit{constructor} \textit{pred}) \textit{clause} ...)} & syntax & \pageref{records_s13} \\
\texttt{(define-syntax \textit{keyword} \textit{expr})} & syntax & \pageref{syntax_s12} \\
\texttt{(delay \textit{expr})} & syntax & \pageref{control_s65} \\
\texttt{(delete-file \textit{path})} & procedure & \pageref{io_s90} \\
\texttt{(denominator \textit{rat})} & procedure & \pageref{objects_s119} \\
\texttt{(display \textit{obj})} & procedure & \pageref{io_s85} \\
\texttt{(display \textit{obj} \textit{textual-output-port})} & procedure & \pageref{io_s85} \\
\texttt{(div \textit{x\textsubscript{1}} \textit{x\textsubscript{2}})} & procedure & \pageref{objects_s99} \\
\texttt{(div-and-mod \textit{x\textsubscript{1}} \textit{x\textsubscript{2}})} & procedure & \pageref{objects_s99} \\
\texttt{(div0 \textit{x\textsubscript{1}} \textit{x\textsubscript{2}})} & procedure & \pageref{objects_s100} \\
\texttt{(div0-and-mod0 \textit{x\textsubscript{1}} \textit{x\textsubscript{2}})} & procedure & \pageref{objects_s100} \\
\texttt{(do ((\textit{var} \textit{init} \textit{update}) ...) (\textit{test} \textit{result} ...) \textit{expr} ...)} & syntax & \pageref{control_s25} \\
\texttt{(dynamic-wind \textit{in} \textit{body} \textit{out})} & procedure & \pageref{control_s56} \\
\texttt{else} & syntax & \pageref{control_s16} \\
\texttt{(endianness \textit{symbol})} & syntax & \pageref{objects_s240} \\
\texttt{(enum-set-\textgreater{}list \textit{enum-set})} & procedure & \pageref{objects_s294} \\
\texttt{(enum-set-complement \textit{enum-set})} & procedure & \pageref{objects_s299} \\
\texttt{(enum-set-constructor \textit{enum-set})} & procedure & \pageref{objects_s292} \\
\texttt{(enum-set-difference \textit{enum-set\textsubscript{1}} \textit{enum-set\textsubscript{2}})} & procedure & \pageref{objects_s298} \\
\texttt{(enum-set-indexer \textit{enum-set})} & procedure & \pageref{objects_s301} \\
\texttt{(enum-set-intersection \textit{enum-set\textsubscript{1}} \textit{enum-set\textsubscript{2}})} & procedure & \pageref{objects_s298} \\
\texttt{(enum-set-member? \textit{symbol} \textit{enum-set})} & procedure & \pageref{objects_s297} \\
\texttt{(enum-set-projection \textit{enum-set\textsubscript{1}} \textit{enum-set\textsubscript{2}})} & procedure & \pageref{objects_s300} \\
\texttt{(enum-set-subset? \textit{enum-set\textsubscript{1}} \textit{enum-set\textsubscript{2}})} & procedure & \pageref{objects_s295} \\
\texttt{(enum-set-union \textit{enum-set\textsubscript{1}} \textit{enum-set\textsubscript{2}})} & procedure & \pageref{objects_s298} \\
\texttt{(enum-set-universe \textit{enum-set})} & procedure & \pageref{objects_s293} \\
\texttt{(enum-set=? \textit{enum-set\textsubscript{1}} \textit{enum-set\textsubscript{2}})} & procedure & \pageref{objects_s296} \\
\texttt{(environment \textit{import-spec} ...)} & procedure & \pageref{control_s81} \\
\texttt{(eof-object)} & procedure & \pageref{io_s54} \\
\texttt{(eof-object? \textit{obj})} & procedure & \pageref{io_s53} \\
\texttt{(eol-style \textit{symbol})} & syntax & \pageref{io_s23} \\
\texttt{(eq? \textit{obj\textsubscript{1}} \textit{obj\textsubscript{2}})} & procedure & \pageref{objects_s10} \\
\texttt{(equal-hash \textit{obj})} & procedure & \pageref{objects_s279} \\
\texttt{(equal? \textit{obj\textsubscript{1}} \textit{obj\textsubscript{2}})} & procedure & \pageref{objects_s13} \\
\texttt{(eqv? \textit{obj\textsubscript{1}} \textit{obj\textsubscript{2}})} & procedure & \pageref{objects_s12} \\
\texttt{(error \textit{who} \textit{msg} \textit{irritant} ...)} & procedure & \pageref{exceptions_s4} \\
\texttt{(error-handling-mode \textit{symbol})} & syntax & \pageref{io_s25} \\
\texttt{(error? \textit{obj})} & procedure & \pageref{exceptions_s22} \\
\texttt{(eval \textit{obj} \textit{environment})} & procedure & \pageref{control_s80} \\
\texttt{(even? \textit{int})} & procedure & \pageref{objects_s96} \\
\texttt{(exact \textit{num})} & procedure & \pageref{objects_s114} \\
\texttt{(exact-\textgreater{}inexact \textit{num})} & procedure & \pageref{objects_s116} \\
\texttt{(exact-integer-sqrt \textit{n})} & procedure & \pageref{objects_s128} \\
\texttt{(exact? \textit{num})} & procedure & \pageref{objects_s86} \\
\texttt{(exists \textit{procedure} \textit{list\textsubscript{1}} \textit{list\textsubscript{2}} ...)} & procedure & \pageref{control_s36} \\
\texttt{(exit)} & procedure & \pageref{libraries_s18} \\
\texttt{(exit \textit{obj})} & procedure & \pageref{libraries_s18} \\
\texttt{(exp \textit{num})} & procedure & \pageref{objects_s129} \\
\texttt{(expt \textit{num\textsubscript{1}} \textit{num\textsubscript{2}})} & procedure & \pageref{objects_s111} \\
\texttt{fields} & syntax & \pageref{records_s16} \\
\texttt{(file-exists? \textit{path})} & procedure & \pageref{io_s89} \\
\texttt{(file-options \textit{symbol} ...)} & syntax & \pageref{io_s26} \\
\texttt{(filter \textit{procedure} \textit{list})} & procedure & \pageref{objects_s55} \\
\texttt{(find \textit{procedure} \textit{list})} & procedure & \pageref{objects_s57} \\
\texttt{(finite? \textit{real})} & procedure & \pageref{objects_s97} \\
\texttt{(fixnum-\textgreater{}flonum \textit{fx})} & procedure & \pageref{objects_s198} \\
\texttt{(fixnum-width)} & procedure & \pageref{objects_s152} \\
\texttt{(fixnum? \textit{obj})} & procedure & \pageref{objects_s150} \\
\texttt{(fl* \textit{fl} ...)} & procedure & \pageref{objects_s186} \\
\texttt{(fl+ \textit{fl} ...)} & procedure & \pageref{objects_s184} \\
\texttt{(fl- \textit{fl})} & procedure & \pageref{objects_s185} \\
\texttt{(fl- \textit{fl\textsubscript{1}} \textit{fl\textsubscript{2}} \textit{fl\textsubscript{3}} ...)} & procedure & \pageref{objects_s185} \\
\texttt{(fl/ \textit{fl})} & procedure & \pageref{objects_s187} \\
\texttt{(fl/ \textit{fl\textsubscript{1}} \textit{fl\textsubscript{2}} \textit{fl\textsubscript{3}} ...)} & procedure & \pageref{objects_s187} \\
\texttt{(fl\textless{}=? \textit{fl\textsubscript{1}} \textit{fl\textsubscript{2}} \textit{fl\textsubscript{3}} ...)} & procedure & \pageref{objects_s178} \\
\texttt{(fl\textless{}? \textit{fl\textsubscript{1}} \textit{fl\textsubscript{2}} \textit{fl\textsubscript{3}} ...)} & procedure & \pageref{objects_s178} \\
\texttt{(fl=? \textit{fl\textsubscript{1}} \textit{fl\textsubscript{2}} \textit{fl\textsubscript{3}} ...)} & procedure & \pageref{objects_s178} \\
\texttt{(fl\textgreater{}=? \textit{fl\textsubscript{1}} \textit{fl\textsubscript{2}} \textit{fl\textsubscript{3}} ...)} & procedure & \pageref{objects_s178} \\
\texttt{(fl\textgreater{}? \textit{fl\textsubscript{1}} \textit{fl\textsubscript{2}} \textit{fl\textsubscript{3}} ...)} & procedure & \pageref{objects_s178} \\
\texttt{(flabs \textit{fl})} & procedure & \pageref{objects_s192} \\
\texttt{(flacos \textit{fl})} & procedure & \pageref{objects_s195} \\
\texttt{(flasin \textit{fl})} & procedure & \pageref{objects_s195} \\
\texttt{(flatan \textit{fl})} & procedure & \pageref{objects_s195} \\
\texttt{(flatan \textit{fl\textsubscript{1}} \textit{fl\textsubscript{2}})} & procedure & \pageref{objects_s195} \\
\texttt{(flceiling \textit{fl})} & procedure & \pageref{objects_s190} \\
\texttt{(flcos \textit{fl})} & procedure & \pageref{objects_s194} \\
\texttt{(fldenominator \textit{fl})} & procedure & \pageref{objects_s191} \\
\texttt{(fldiv \textit{fl\textsubscript{1}} \textit{fl\textsubscript{2}})} & procedure & \pageref{objects_s188} \\
\texttt{(fldiv-and-mod \textit{fl\textsubscript{1}} \textit{fl\textsubscript{2}})} & procedure & \pageref{objects_s188} \\
\texttt{(fldiv0 \textit{fl\textsubscript{1}} \textit{fl\textsubscript{2}})} & procedure & \pageref{objects_s189} \\
\texttt{(fldiv0-and-mod0 \textit{fl\textsubscript{1}} \textit{fl\textsubscript{2}})} & procedure & \pageref{objects_s189} \\
\texttt{(fleven? \textit{fl-int})} & procedure & \pageref{objects_s182} \\
\texttt{(flexp \textit{fl})} & procedure & \pageref{objects_s193} \\
\texttt{(flexpt \textit{fl\textsubscript{1}} \textit{fl\textsubscript{2}})} & procedure & \pageref{objects_s197} \\
\texttt{(flfinite? \textit{fl})} & procedure & \pageref{objects_s181} \\
\texttt{(flfloor \textit{fl})} & procedure & \pageref{objects_s190} \\
\texttt{(flinfinite? \textit{fl})} & procedure & \pageref{objects_s181} \\
\texttt{(flinteger? \textit{fl})} & procedure & \pageref{objects_s180} \\
\texttt{(fllog \textit{fl})} & procedure & \pageref{objects_s193} \\
\texttt{(fllog \textit{fl\textsubscript{1}} \textit{fl\textsubscript{2}})} & procedure & \pageref{objects_s193} \\
\texttt{(flmax \textit{fl\textsubscript{1}} \textit{fl\textsubscript{2}} ...)} & procedure & \pageref{objects_s183} \\
\texttt{(flmin \textit{fl\textsubscript{1}} \textit{fl\textsubscript{2}} ...)} & procedure & \pageref{objects_s183} \\
\texttt{(flmod \textit{fl\textsubscript{1}} \textit{fl\textsubscript{2}})} & procedure & \pageref{objects_s188} \\
\texttt{(flmod0 \textit{fl\textsubscript{1}} \textit{fl\textsubscript{2}})} & procedure & \pageref{objects_s189} \\
\texttt{(flnan? \textit{fl})} & procedure & \pageref{objects_s181} \\
\texttt{(flnegative? \textit{fl})} & procedure & \pageref{objects_s179} \\
\texttt{(flnumerator \textit{fl})} & procedure & \pageref{objects_s191} \\
\texttt{(flodd? \textit{fl-int})} & procedure & \pageref{objects_s182} \\
\texttt{(flonum? \textit{obj})} & procedure & \pageref{objects_s177} \\
\texttt{(floor \textit{real})} & procedure & \pageref{objects_s102} \\
\texttt{(flpositive? \textit{fl})} & procedure & \pageref{objects_s179} \\
\texttt{(flround \textit{fl})} & procedure & \pageref{objects_s190} \\
\texttt{(flsin \textit{fl})} & procedure & \pageref{objects_s194} \\
\texttt{(flsqrt \textit{fl})} & procedure & \pageref{objects_s196} \\
\texttt{(fltan \textit{fl})} & procedure & \pageref{objects_s194} \\
\texttt{(fltruncate \textit{fl})} & procedure & \pageref{objects_s190} \\
\texttt{(flush-output-port \textit{output-port})} & procedure & \pageref{io_s74} \\
\texttt{(flzero? \textit{fl})} & procedure & \pageref{objects_s179} \\
\texttt{(fold-left \textit{procedure} \textit{obj} \textit{list\textsubscript{1}} \textit{list\textsubscript{2}} ...)} & procedure & \pageref{control_s38} \\
\texttt{(fold-right \textit{procedure} \textit{obj} \textit{list\textsubscript{1}} \textit{list\textsubscript{2}} ...)} & procedure & \pageref{control_s41} \\
\texttt{(for-all \textit{procedure} \textit{list\textsubscript{1}} \textit{list\textsubscript{2}} ...)} & procedure & \pageref{control_s37} \\
\texttt{(for-each \textit{procedure} \textit{list\textsubscript{1}} \textit{list\textsubscript{2}} ...)} & procedure & \pageref{control_s33} \\
\texttt{(force \textit{promise})} & procedure & \pageref{control_s65} \\
\texttt{(free-identifier=? \textit{identifier\textsubscript{1}} \textit{identifier\textsubscript{2}})} & procedure & \pageref{syntax_s37} \\
\texttt{(fx* \textit{fx\textsubscript{1}} \textit{fx\textsubscript{2}})} & procedure & \pageref{objects_s159} \\
\texttt{(fx*/carry \textit{fx\textsubscript{1}} \textit{fx\textsubscript{2}} \textit{fx\textsubscript{3}})} & procedure & \pageref{objects_s162} \\
\texttt{(fx+ \textit{fx\textsubscript{1}} \textit{fx\textsubscript{2}})} & procedure & \pageref{objects_s157} \\
\texttt{(fx+/carry \textit{fx\textsubscript{1}} \textit{fx\textsubscript{2}} \textit{fx\textsubscript{3}})} & procedure & \pageref{objects_s162} \\
\texttt{(fx- \textit{fx})} & procedure & \pageref{objects_s158} \\
\texttt{(fx- \textit{fx\textsubscript{1}} \textit{fx\textsubscript{2}})} & procedure & \pageref{objects_s158} \\
\texttt{(fx-/carry \textit{fx\textsubscript{1}} \textit{fx\textsubscript{2}} \textit{fx\textsubscript{3}})} & procedure & \pageref{objects_s162} \\
\texttt{(fx\textless{}=? \textit{fx\textsubscript{1}} \textit{fx\textsubscript{2}} \textit{fx\textsubscript{3}} ...)} & procedure & \pageref{objects_s153} \\
\texttt{(fx\textless{}? \textit{fx\textsubscript{1}} \textit{fx\textsubscript{2}} \textit{fx\textsubscript{3}} ...)} & procedure & \pageref{objects_s153} \\
\texttt{(fx=? \textit{fx\textsubscript{1}} \textit{fx\textsubscript{2}} \textit{fx\textsubscript{3}} ...)} & procedure & \pageref{objects_s153} \\
\texttt{(fx\textgreater{}=? \textit{fx\textsubscript{1}} \textit{fx\textsubscript{2}} \textit{fx\textsubscript{3}} ...)} & procedure & \pageref{objects_s153} \\
\texttt{(fx\textgreater{}? \textit{fx\textsubscript{1}} \textit{fx\textsubscript{2}} \textit{fx\textsubscript{3}} ...)} & procedure & \pageref{objects_s153} \\
\texttt{(fxand \textit{fx} ...)} & procedure & \pageref{objects_s163} \\
\texttt{(fxarithmetic-shift \textit{fx\textsubscript{1}} \textit{fx\textsubscript{2}})} & procedure & \pageref{objects_s173} \\
\texttt{(fxarithmetic-shift-left \textit{fx\textsubscript{1}} \textit{fx\textsubscript{2}})} & procedure & \pageref{objects_s172} \\
\texttt{(fxarithmetic-shift-right \textit{fx\textsubscript{1}} \textit{fx\textsubscript{2}})} & procedure & \pageref{objects_s172} \\
\texttt{(fxbit-count \textit{fx})} & procedure & \pageref{objects_s165} \\
\texttt{(fxbit-field \textit{fx\textsubscript{1}} \textit{fx\textsubscript{2}} \textit{fx\textsubscript{3}})} & procedure & \pageref{objects_s170} \\
\texttt{(fxbit-set? \textit{fx\textsubscript{1}} \textit{fx\textsubscript{2}})} & procedure & \pageref{objects_s168} \\
\texttt{(fxcopy-bit \textit{fx\textsubscript{1}} \textit{fx\textsubscript{2}} \textit{fx\textsubscript{3}})} & procedure & \pageref{objects_s169} \\
\texttt{(fxcopy-bit-field \textit{fx\textsubscript{1}} \textit{fx\textsubscript{2}} \textit{fx\textsubscript{3}} \textit{fx\textsubscript{4}})} & procedure & \pageref{objects_s171} \\
\texttt{(fxdiv \textit{fx\textsubscript{1}} \textit{fx\textsubscript{2}})} & procedure & \pageref{objects_s160} \\
\texttt{(fxdiv-and-mod \textit{fx\textsubscript{1}} \textit{fx\textsubscript{2}})} & procedure & \pageref{objects_s160} \\
\texttt{(fxdiv0 \textit{fx\textsubscript{1}} \textit{fx\textsubscript{2}})} & procedure & \pageref{objects_s161} \\
\texttt{(fxdiv0-and-mod0 \textit{fx\textsubscript{1}} \textit{fx\textsubscript{2}})} & procedure & \pageref{objects_s161} \\
\texttt{(fxeven? \textit{fx})} & procedure & \pageref{objects_s155} \\
\texttt{(fxfirst-bit-set \textit{fx})} & procedure & \pageref{objects_s167} \\
\texttt{(fxif \textit{fx\textsubscript{1}} \textit{fx\textsubscript{2}} \textit{fx\textsubscript{3}})} & procedure & \pageref{objects_s164} \\
\texttt{(fxior \textit{fx} ...)} & procedure & \pageref{objects_s163} \\
\texttt{(fxlength \textit{fx})} & procedure & \pageref{objects_s166} \\
\texttt{(fxmax \textit{fx\textsubscript{1}} \textit{fx\textsubscript{2}} ...)} & procedure & \pageref{objects_s156} \\
\texttt{(fxmin \textit{fx\textsubscript{1}} \textit{fx\textsubscript{2}} ...)} & procedure & \pageref{objects_s156} \\
\texttt{(fxmod \textit{fx\textsubscript{1}} \textit{fx\textsubscript{2}})} & procedure & \pageref{objects_s160} \\
\texttt{(fxmod0 \textit{fx\textsubscript{1}} \textit{fx\textsubscript{2}})} & procedure & \pageref{objects_s161} \\
\texttt{(fxnegative? \textit{fx})} & procedure & \pageref{objects_s154} \\
\texttt{(fxnot \textit{fx})} & procedure & \pageref{objects_s163} \\
\texttt{(fxodd? \textit{fx})} & procedure & \pageref{objects_s155} \\
\texttt{(fxpositive? \textit{fx})} & procedure & \pageref{objects_s154} \\
\texttt{(fxreverse-bit-field \textit{fx\textsubscript{1}} \textit{fx\textsubscript{2}} \textit{fx\textsubscript{3}})} & procedure & \pageref{objects_s175} \\
\texttt{(fxrotate-bit-field \textit{fx\textsubscript{1}} \textit{fx\textsubscript{2}} \textit{fx\textsubscript{3}} \textit{fx\textsubscript{4}})} & procedure & \pageref{objects_s174} \\
\texttt{(fxxor \textit{fx} ...)} & procedure & \pageref{objects_s163} \\
\texttt{(fxzero? \textit{fx})} & procedure & \pageref{objects_s154} \\
\texttt{(gcd \textit{int} ...)} & procedure & \pageref{objects_s109} \\
\texttt{(generate-temporaries \textit{list})} & procedure & \pageref{syntax_s49} \\
\texttt{(get-bytevector-all \textit{binary-input-port})} & procedure & \pageref{io_s60} \\
\texttt{(get-bytevector-n \textit{binary-input-port} \textit{n})} & procedure & \pageref{io_s57} \\
\texttt{(get-bytevector-n! \textit{binary-input-port} \textit{bytevector} \textit{start} \textit{n})} & procedure & \pageref{io_s58} \\
\texttt{(get-bytevector-some \textit{binary-input-port})} & procedure & \pageref{io_s59} \\
\texttt{(get-char \textit{textual-input-port})} & procedure & \pageref{io_s61} \\
\texttt{(get-datum \textit{textual-input-port})} & procedure & \pageref{io_s67} \\
\texttt{(get-line \textit{textual-input-port})} & procedure & \pageref{io_s66} \\
\texttt{(get-string-all \textit{textual-input-port})} & procedure & \pageref{io_s65} \\
\texttt{(get-string-n \textit{textual-input-port} \textit{n})} & procedure & \pageref{io_s63} \\
\texttt{(get-string-n! \textit{textual-input-port} \textit{string} \textit{start} \textit{n})} & procedure & \pageref{io_s64} \\
\texttt{(get-u8 \textit{binary-input-port})} & procedure & \pageref{io_s55} \\
\texttt{(greatest-fixnum)} & procedure & \pageref{objects_s151} \\
\texttt{(guard (\textit{var} \textit{clause\textsubscript{1}} \textit{clause\textsubscript{2}} ...) \textit{b1} \textit{b2} ...)} & syntax & \pageref{exceptions_s8} \\
\texttt{(hashtable-clear! \textit{hashtable})} & procedure & \pageref{objects_s287} \\
\texttt{(hashtable-clear! \textit{hashtable} \textit{size})} & procedure & \pageref{objects_s287} \\
\texttt{(hashtable-contains? \textit{hashtable} \textit{key})} & procedure & \pageref{objects_s282} \\
\texttt{(hashtable-copy \textit{hashtable})} & procedure & \pageref{objects_s286} \\
\texttt{(hashtable-copy \textit{hashtable} \textit{mutable?})} & procedure & \pageref{objects_s286} \\
\texttt{(hashtable-delete! \textit{hashtable} \textit{key})} & procedure & \pageref{objects_s284} \\
\texttt{(hashtable-entries \textit{hashtable})} & procedure & \pageref{objects_s289} \\
\texttt{(hashtable-equivalence-function \textit{hashtable})} & procedure & \pageref{objects_s278} \\
\texttt{(hashtable-hash-function \textit{hashtable})} & procedure & \pageref{objects_s278} \\
\texttt{(hashtable-keys \textit{hashtable})} & procedure & \pageref{objects_s288} \\
\texttt{(hashtable-mutable? \textit{hashtable})} & procedure & \pageref{objects_s277} \\
\texttt{(hashtable-ref \textit{hashtable} \textit{key} \textit{default})} & procedure & \pageref{objects_s281} \\
\texttt{(hashtable-set! \textit{hashtable} \textit{key} \textit{obj})} & procedure & \pageref{objects_s280} \\
\texttt{(hashtable-size \textit{hashtable})} & procedure & \pageref{objects_s285} \\
\texttt{(hashtable-update! \textit{hashtable} \textit{key} \textit{procedure} \textit{default})} & procedure & \pageref{objects_s283} \\
\texttt{(hashtable? \textit{obj})} & procedure & \pageref{objects_s25} \\
\texttt{(i/o-decoding-error? \textit{obj})} & procedure & \pageref{exceptions_s42} \\
\texttt{(i/o-encoding-error-char \textit{condition})} & procedure & \pageref{exceptions_s43} \\
\texttt{(i/o-encoding-error? \textit{obj})} & procedure & \pageref{exceptions_s43} \\
\texttt{(i/o-error-filename \textit{condition})} & procedure & \pageref{exceptions_s36} \\
\texttt{(i/o-error-port \textit{condition})} & procedure & \pageref{exceptions_s41} \\
\texttt{(i/o-error-position \textit{condition})} & procedure & \pageref{exceptions_s35} \\
\texttt{(i/o-error? \textit{obj})} & procedure & \pageref{exceptions_s32} \\
\texttt{(i/o-file-already-exists-error? \textit{obj})} & procedure & \pageref{exceptions_s39} \\
\texttt{(i/o-file-does-not-exist-error? \textit{obj})} & procedure & \pageref{exceptions_s40} \\
\texttt{(i/o-file-is-read-only-error? \textit{obj})} & procedure & \pageref{exceptions_s38} \\
\texttt{(i/o-file-protection-error? \textit{obj})} & procedure & \pageref{exceptions_s37} \\
\texttt{(i/o-filename-error? \textit{obj})} & procedure & \pageref{exceptions_s36} \\
\texttt{(i/o-invalid-position-error? \textit{obj})} & procedure & \pageref{exceptions_s35} \\
\texttt{(i/o-port-error? \textit{obj})} & procedure & \pageref{exceptions_s41} \\
\texttt{(i/o-read-error? \textit{obj})} & procedure & \pageref{exceptions_s33} \\
\texttt{(i/o-write-error? \textit{obj})} & procedure & \pageref{exceptions_s34} \\
\texttt{(identifier-syntax \textit{tmpl})} & syntax & \pageref{syntax_s27} \\
\texttt{(identifier-syntax (\textit{id\textsubscript{1}} \textit{tmpl\textsubscript{1}}) ((set! \textit{id\textsubscript{2}} \textit{e\textsubscript{2}}) \textit{tmpl\textsubscript{2}}))} & syntax & \pageref{syntax_s27} \\
\texttt{(identifier? \textit{obj})} & procedure & \pageref{syntax_s35} \\
\texttt{(if \textit{test} \textit{consequent} \textit{alternative})} & syntax & \pageref{control_s8} \\
\texttt{(if \textit{test} \textit{consequent})} & syntax & \pageref{control_s8} \\
\texttt{(imag-part \textit{num})} & procedure & \pageref{objects_s121} \\
\texttt{immutable} & syntax & \pageref{records_s16} \\
\texttt{(implementation-restriction-violation? \textit{obj})} & procedure & \pageref{exceptions_s28} \\
\texttt{(inexact \textit{num})} & procedure & \pageref{objects_s112} \\
\texttt{(inexact-\textgreater{}exact \textit{num})} & procedure & \pageref{objects_s116} \\
\texttt{(inexact? \textit{num})} & procedure & \pageref{objects_s87} \\
\texttt{(infinite? \textit{real})} & procedure & \pageref{objects_s97} \\
\texttt{(input-port? \textit{obj})} & procedure & \pageref{io_s44} \\
\texttt{(integer-\textgreater{}char \textit{n})} & procedure & \pageref{objects_s211} \\
\texttt{(integer-valued? \textit{obj})} & procedure & \pageref{objects_s18} \\
\texttt{(integer? \textit{obj})} & procedure & \pageref{objects_s17} \\
\texttt{(irritants-condition? \textit{obj})} & procedure & \pageref{exceptions_s25} \\
\texttt{(lambda \textit{formals} \textit{body\textsubscript{1}} \textit{body\textsubscript{2}} ...)} & syntax & \pageref{binding_s3} \\
\texttt{(latin-1-codec)} & procedure & \pageref{io_s22} \\
\texttt{(lcm \textit{int} ...)} & procedure & \pageref{objects_s110} \\
\texttt{(least-fixnum)} & procedure & \pageref{objects_s151} \\
\texttt{(length \textit{list})} & procedure & \pageref{objects_s46} \\
\texttt{(let ((\textit{var} \textit{expr}) ...) \textit{body\textsubscript{1}} \textit{body\textsubscript{2}} ...)} & syntax & \pageref{binding_s16} \\
\texttt{(let \textit{name} ((\textit{var} \textit{expr}) ...) \textit{body\textsubscript{1}} \textit{body\textsubscript{2}} ...)} & syntax & \pageref{control_s20} \\
\texttt{(let* ((\textit{var} \textit{expr}) ...) \textit{body\textsubscript{1}} \textit{body\textsubscript{2}} ...)} & syntax & \pageref{binding_s18} \\
\texttt{(let*-values ((\textit{formals} \textit{expr}) ...) \textit{body\textsubscript{1}} \textit{body\textsubscript{2}} ...)} & syntax & \pageref{binding_s23} \\
\texttt{(let-syntax ((\textit{keyword} \textit{expr}) ...) \textit{form\textsubscript{1}} \textit{form\textsubscript{2}} ...)} & syntax & \pageref{syntax_s13} \\
\texttt{(let-values ((\textit{formals} \textit{expr}) ...) \textit{body\textsubscript{1}} \textit{body\textsubscript{2}} ...)} & syntax & \pageref{binding_s23} \\
\texttt{(letrec ((\textit{var} \textit{expr}) ...) \textit{body\textsubscript{1}} \textit{body\textsubscript{2}} ...)} & syntax & \pageref{binding_s20} \\
\texttt{(letrec* ((\textit{var} \textit{expr}) ...) \textit{body\textsubscript{1}} \textit{body\textsubscript{2}} ...)} & syntax & \pageref{binding_s22} \\
\texttt{(letrec-syntax ((\textit{keyword} \textit{expr}) ...) \textit{form\textsubscript{1}} \textit{form\textsubscript{2}} ...)} & syntax & \pageref{syntax_s13} \\
\texttt{(lexical-violation? \textit{obj})} & procedure & \pageref{exceptions_s29} \\
\texttt{(list \textit{obj} ...)} & procedure & \pageref{objects_s43} \\
\texttt{(list-\textgreater{}string \textit{list})} & procedure & \pageref{objects_s229} \\
\texttt{(list-\textgreater{}vector \textit{list})} & procedure & \pageref{objects_s238} \\
\texttt{(list-ref \textit{list} \textit{n})} & procedure & \pageref{objects_s47} \\
\texttt{(list-sort \textit{predicate} \textit{list})} & procedure & \pageref{objects_s62} \\
\texttt{(list-tail \textit{list} \textit{n})} & procedure & \pageref{objects_s48} \\
\texttt{(list? \textit{obj})} & procedure & \pageref{objects_s45} \\
\texttt{(log \textit{num})} & procedure & \pageref{objects_s130} \\
\texttt{(log \textit{num\textsubscript{1}} \textit{num\textsubscript{2}})} & procedure & \pageref{objects_s130} \\
\texttt{(lookahead-char \textit{textual-input-port})} & procedure & \pageref{io_s62} \\
\texttt{(lookahead-u8 \textit{binary-input-port})} & procedure & \pageref{io_s56} \\
\texttt{(magnitude \textit{num})} & procedure & \pageref{objects_s125} \\
\texttt{(make-assertion-violation)} & procedure & \pageref{exceptions_s21} \\
\texttt{(make-bytevector \textit{n})} & procedure & \pageref{objects_s242} \\
\texttt{(make-bytevector \textit{n} \textit{fill})} & procedure & \pageref{objects_s242} \\
\texttt{(make-custom-binary-input-port \textit{id} \textit{r!} \textit{gp} \textit{sp!} \textit{close})} & procedure & \pageref{io_s41} \\
\texttt{(make-custom-binary-input/output-port \textit{id} \textit{r!} \textit{w!} \textit{gp} \textit{sp!} \textit{close})} & procedure & \pageref{io_s41} \\
\texttt{(make-custom-binary-output-port \textit{id} \textit{w!} \textit{gp} \textit{sp!} \textit{close})} & procedure & \pageref{io_s41} \\
\texttt{(make-custom-textual-input-port \textit{id} \textit{r!} \textit{gp} \textit{sp!} \textit{close})} & procedure & \pageref{io_s42} \\
\texttt{(make-custom-textual-input/output-port \textit{id} \textit{r!} \textit{w!} \textit{gp} \textit{sp!} \textit{close})} & procedure & \pageref{io_s42} \\
\texttt{(make-custom-textual-output-port \textit{id} \textit{w!} \textit{gp} \textit{sp!} \textit{close})} & procedure & \pageref{io_s42} \\
\texttt{(make-enumeration \textit{symbol-list})} & procedure & \pageref{objects_s291} \\
\texttt{(make-eq-hashtable)} & procedure & \pageref{objects_s274} \\
\texttt{(make-eq-hashtable \textit{size})} & procedure & \pageref{objects_s274} \\
\texttt{(make-eqv-hashtable)} & procedure & \pageref{objects_s275} \\
\texttt{(make-eqv-hashtable \textit{size})} & procedure & \pageref{objects_s275} \\
\texttt{(make-error)} & procedure & \pageref{exceptions_s22} \\
\texttt{(make-hashtable \textit{hash} \textit{equiv?})} & procedure & \pageref{objects_s276} \\
\texttt{(make-hashtable \textit{hash} \textit{equiv?} \textit{size})} & procedure & \pageref{objects_s276} \\
\texttt{(make-i/o-decoding-error \textit{pobj})} & procedure & \pageref{exceptions_s42} \\
\texttt{(make-i/o-encoding-error \textit{pobj} \textit{cobj})} & procedure & \pageref{exceptions_s43} \\
\texttt{(make-i/o-error)} & procedure & \pageref{exceptions_s32} \\
\texttt{(make-i/o-file-already-exists-error \textit{filename})} & procedure & \pageref{exceptions_s39} \\
\texttt{(make-i/o-file-does-not-exist-error \textit{filename})} & procedure & \pageref{exceptions_s40} \\
\texttt{(make-i/o-file-is-read-only-error \textit{filename})} & procedure & \pageref{exceptions_s38} \\
\texttt{(make-i/o-file-protection-error \textit{filename})} & procedure & \pageref{exceptions_s37} \\
\texttt{(make-i/o-filename-error \textit{filename})} & procedure & \pageref{exceptions_s36} \\
\texttt{(make-i/o-invalid-position-error \textit{position})} & procedure & \pageref{exceptions_s35} \\
\texttt{(make-i/o-port-error \textit{pobj})} & procedure & \pageref{exceptions_s41} \\
\texttt{(make-i/o-read-error)} & procedure & \pageref{exceptions_s33} \\
\texttt{(make-i/o-write-error)} & procedure & \pageref{exceptions_s34} \\
\texttt{(make-implementation-restriction-violation)} & procedure & \pageref{exceptions_s28} \\
\texttt{(make-irritants-condition \textit{irritants})} & procedure & \pageref{exceptions_s25} \\
\texttt{(make-lexical-violation)} & procedure & \pageref{exceptions_s29} \\
\texttt{(make-message-condition \textit{message})} & procedure & \pageref{exceptions_s24} \\
\texttt{(make-no-infinities-violation)} & procedure & \pageref{exceptions_s44} \\
\texttt{(make-no-nans-violation)} & procedure & \pageref{exceptions_s45} \\
\texttt{(make-non-continuable-violation)} & procedure & \pageref{exceptions_s27} \\
\texttt{(make-polar \textit{real\textsubscript{1}} \textit{real\textsubscript{2}})} & procedure & \pageref{objects_s123} \\
\texttt{(make-record-constructor-descriptor \textit{rtd} \textit{parent-rcd} \textit{protocol})} & procedure & \pageref{records_s24} \\
\texttt{(make-record-type-descriptor \textit{name} \textit{parent} \textit{uid} \textit{s?} \textit{o?} \textit{fields})} & procedure & \pageref{records_s20} \\
\texttt{(make-rectangular \textit{real\textsubscript{1}} \textit{real\textsubscript{2}})} & procedure & \pageref{objects_s122} \\
\texttt{(make-serious-condition)} & procedure & \pageref{exceptions_s19} \\
\texttt{(make-string \textit{n})} & procedure & \pageref{objects_s218} \\
\texttt{(make-string \textit{n} \textit{char})} & procedure & \pageref{objects_s218} \\
\texttt{(make-syntax-violation \textit{form} \textit{subform})} & procedure & \pageref{exceptions_s30} \\
\texttt{(make-transcoder \textit{codec})} & procedure & \pageref{io_s19} \\
\texttt{(make-transcoder \textit{codec} \textit{eol-style})} & procedure & \pageref{io_s19} \\
\texttt{(make-transcoder \textit{codec} \textit{eol-style} \textit{error-handling-mode})} & procedure & \pageref{io_s19} \\
\texttt{(make-undefined-violation)} & procedure & \pageref{exceptions_s31} \\
\texttt{(make-variable-transformer \textit{procedure})} & procedure & \pageref{syntax_s42} \\
\texttt{(make-vector \textit{n})} & procedure & \pageref{objects_s232} \\
\texttt{(make-vector \textit{n} \textit{obj})} & procedure & \pageref{objects_s232} \\
\texttt{(make-violation)} & procedure & \pageref{exceptions_s20} \\
\texttt{(make-warning)} & procedure & \pageref{exceptions_s23} \\
\texttt{(make-who-condition \textit{who})} & procedure & \pageref{exceptions_s26} \\
\texttt{(map \textit{procedure} \textit{list\textsubscript{1}} \textit{list\textsubscript{2}} ...)} & procedure & \pageref{control_s30} \\
\texttt{(max \textit{real\textsubscript{1}} \textit{real\textsubscript{2}} ...)} & procedure & \pageref{objects_s107} \\
\texttt{(member \textit{obj} \textit{list})} & procedure & \pageref{objects_s51} \\
\texttt{(memp \textit{procedure} \textit{list})} & procedure & \pageref{objects_s52} \\
\texttt{(memq \textit{obj} \textit{list})} & procedure & \pageref{objects_s51} \\
\texttt{(memv \textit{obj} \textit{list})} & procedure & \pageref{objects_s51} \\
\texttt{(message-condition? \textit{obj})} & procedure & \pageref{exceptions_s24} \\
\texttt{(min \textit{real\textsubscript{1}} \textit{real\textsubscript{2}} ...)} & procedure & \pageref{objects_s108} \\
\texttt{(mod \textit{x\textsubscript{1}} \textit{x\textsubscript{2}})} & procedure & \pageref{objects_s99} \\
\texttt{(mod0 \textit{x\textsubscript{1}} \textit{x\textsubscript{2}})} & procedure & \pageref{objects_s100} \\
\texttt{(modulo \textit{int\textsubscript{1}} \textit{int\textsubscript{2}})} & procedure & \pageref{objects_s98} \\
\texttt{mutable} & syntax & \pageref{records_s16} \\
\texttt{(nan? \textit{real})} & procedure & \pageref{objects_s97} \\
\texttt{(native-endianness)} & procedure & \pageref{objects_s241} \\
\texttt{(native-eol-style)} & procedure & \pageref{io_s24} \\
\texttt{(native-transcoder)} & procedure & \pageref{io_s21} \\
\texttt{(negative? \textit{real})} & procedure & \pageref{objects_s95} \\
\texttt{(newline)} & procedure & \pageref{io_s87} \\
\texttt{(newline \textit{textual-output-port})} & procedure & \pageref{io_s87} \\
\texttt{(no-infinities-violation? \textit{obj})} & procedure & \pageref{exceptions_s44} \\
\texttt{(no-nans-violation? \textit{obj})} & procedure & \pageref{exceptions_s45} \\
\texttt{(non-continuable-violation? \textit{obj})} & procedure & \pageref{exceptions_s27} \\
\texttt{nongenerative} & syntax & \pageref{records_s16} \\
\texttt{(not \textit{obj})} & procedure & \pageref{control_s10} \\
\texttt{(null-environment \textit{version})} & procedure & \pageref{control_s82} \\
\texttt{(null? \textit{obj})} & procedure & \pageref{objects_s15} \\
\texttt{(number-\textgreater{}string \textit{num})} & procedure & \pageref{objects_s148} \\
\texttt{(number-\textgreater{}string \textit{num} \textit{radix})} & procedure & \pageref{objects_s148} \\
\texttt{(number-\textgreater{}string \textit{num} \textit{radix} \textit{precision})} & procedure & \pageref{objects_s148} \\
\texttt{(number? \textit{obj})} & procedure & \pageref{objects_s17} \\
\texttt{(numerator \textit{rat})} & procedure & \pageref{objects_s118} \\
\texttt{(odd? \textit{int})} & procedure & \pageref{objects_s96} \\
\texttt{opaque} & syntax & \pageref{records_s16} \\
\texttt{(open-bytevector-input-port \textit{bytevector})} & procedure & \pageref{io_s34} \\
\texttt{(open-bytevector-input-port \textit{bytevector} \textit{?transcoder})} & procedure & \pageref{io_s34} \\
\texttt{(open-bytevector-output-port)} & procedure & \pageref{io_s36} \\
\texttt{(open-bytevector-output-port \textit{?transcoder})} & procedure & \pageref{io_s36} \\
\texttt{(open-file-input-port \textit{path})} & procedure & \pageref{io_s29} \\
\texttt{(open-file-input-port \textit{path} \textit{options})} & procedure & \pageref{io_s29} \\
\texttt{(open-file-input-port \textit{path} \textit{options} \textit{b-mode})} & procedure & \pageref{io_s29} \\
\texttt{(open-file-input-port \textit{path} \textit{options} \textit{b-mode} \textit{?transcoder})} & procedure & \pageref{io_s29} \\
\texttt{(open-file-input/output-port \textit{path})} & procedure & \pageref{io_s31} \\
\texttt{(open-file-input/output-port \textit{path} \textit{options})} & procedure & \pageref{io_s31} \\
\texttt{(open-file-input/output-port \textit{path} \textit{options} \textit{b-mode})} & procedure & \pageref{io_s31} \\
\texttt{(open-file-input/output-port \textit{path} \textit{options} \textit{b-mode} \textit{?transcoder})} & procedure & \pageref{io_s31} \\
\texttt{(open-file-output-port \textit{path})} & procedure & \pageref{io_s30} \\
\texttt{(open-file-output-port \textit{path} \textit{options})} & procedure & \pageref{io_s30} \\
\texttt{(open-file-output-port \textit{path} \textit{options} \textit{b-mode})} & procedure & \pageref{io_s30} \\
\texttt{(open-file-output-port \textit{path} \textit{options} \textit{b-mode} \textit{?transcoder})} & procedure & \pageref{io_s30} \\
\texttt{(open-input-file \textit{path})} & procedure & \pageref{io_s75} \\
\texttt{(open-output-file \textit{path})} & procedure & \pageref{io_s76} \\
\texttt{(open-string-input-port \textit{string})} & procedure & \pageref{io_s35} \\
\texttt{(open-string-output-port)} & procedure & \pageref{io_s37} \\
\texttt{(or \textit{expr} ...)} & syntax & \pageref{control_s12} \\
\texttt{(output-port-buffer-mode \textit{port})} & procedure & \pageref{io_s52} \\
\texttt{(output-port? \textit{obj})} & procedure & \pageref{io_s44} \\
\texttt{(pair? \textit{obj})} & procedure & \pageref{objects_s16} \\
\texttt{parent} & syntax & \pageref{records_s16} \\
\texttt{parent-rtd} & syntax & \pageref{records_s16} \\
\texttt{(partition \textit{procedure} \textit{list})} & procedure & \pageref{objects_s56} \\
\texttt{(peek-char)} & procedure & \pageref{io_s83} \\
\texttt{(peek-char \textit{textual-input-port})} & procedure & \pageref{io_s83} \\
\texttt{(port-eof? \textit{input-port})} & procedure & \pageref{io_s68} \\
\texttt{(port-has-port-position? \textit{port})} & procedure & \pageref{io_s49} \\
\texttt{(port-has-set-port-position!? \textit{port})} & procedure & \pageref{io_s50} \\
\texttt{(port-position \textit{port})} & procedure & \pageref{io_s49} \\
\texttt{(port-transcoder \textit{port})} & procedure & \pageref{io_s48} \\
\texttt{(port? \textit{obj})} & procedure & \pageref{io_s43} \\
\texttt{(positive? \textit{real})} & procedure & \pageref{objects_s94} \\
\texttt{(\textit{expr\textsubscript{0}} \textit{expr\textsubscript{1}} ...)} & syntax & \pageref{control_s1} \\
\texttt{(procedure? \textit{obj})} & procedure & \pageref{objects_s23} \\
\texttt{protocol} & syntax & \pageref{records_s16} \\
\texttt{(put-bytevector \textit{binary-output-port} \textit{bytevector})} & procedure & \pageref{io_s70} \\
\texttt{(put-bytevector \textit{binary-output-port} \textit{bytevector} \textit{start})} & procedure & \pageref{io_s70} \\
\texttt{(put-bytevector \textit{binary-output-port} \textit{bytevector} \textit{start} \textit{n})} & procedure & \pageref{io_s70} \\
\texttt{(put-char \textit{textual-output-port} \textit{char})} & procedure & \pageref{io_s71} \\
\texttt{(put-datum \textit{textual-output-port} \textit{obj})} & procedure & \pageref{io_s73} \\
\texttt{(put-string \textit{textual-output-port} \textit{string})} & procedure & \pageref{io_s72} \\
\texttt{(put-string \textit{textual-output-port} \textit{string} \textit{start})} & procedure & \pageref{io_s72} \\
\texttt{(put-string \textit{textual-output-port} \textit{string} \textit{start} \textit{n})} & procedure & \pageref{io_s72} \\
\texttt{(put-u8 \textit{binary-output-port} \textit{octet})} & procedure & \pageref{io_s69} \\
\texttt{(quasiquote \textit{obj} ...)} & syntax & \pageref{objects_s5} \\
\texttt{(quasisyntax \textit{template} ...)} & syntax & \pageref{syntax_s40} \\
\texttt{(quote \textit{obj})} & syntax & \pageref{objects_s2} \\
\texttt{(quotient \textit{int\textsubscript{1}} \textit{int\textsubscript{2}})} & procedure & \pageref{objects_s98} \\
\texttt{(raise \textit{obj})} & procedure & \pageref{exceptions_s3} \\
\texttt{(raise-continuable \textit{obj})} & procedure & \pageref{exceptions_s3} \\
\texttt{(rational-valued? \textit{obj})} & procedure & \pageref{objects_s18} \\
\texttt{(rational? \textit{obj})} & procedure & \pageref{objects_s17} \\
\texttt{(rationalize \textit{real\textsubscript{1}} \textit{real\textsubscript{2}})} & procedure & \pageref{objects_s117} \\
\texttt{(read)} & procedure & \pageref{io_s81} \\
\texttt{(read \textit{textual-input-port})} & procedure & \pageref{io_s81} \\
\texttt{(read-char)} & procedure & \pageref{io_s82} \\
\texttt{(read-char \textit{textual-input-port})} & procedure & \pageref{io_s82} \\
\texttt{(real-\textgreater{}flonum \textit{real})} & procedure & \pageref{objects_s198} \\
\texttt{(real-part \textit{num})} & procedure & \pageref{objects_s120} \\
\texttt{(real-valued? \textit{obj})} & procedure & \pageref{objects_s18} \\
\texttt{(real? \textit{obj})} & procedure & \pageref{objects_s17} \\
\texttt{(record-accessor \textit{rtd} \textit{idx})} & procedure & \pageref{records_s31} \\
\texttt{(record-constructor \textit{rcd})} & procedure & \pageref{records_s29} \\
\texttt{(record-constructor-descriptor \textit{record-name})} & syntax & \pageref{records_s28} \\
\texttt{(record-field-mutable? \textit{rtd} \textit{idx})} & procedure & \pageref{records_s39} \\
\texttt{(record-mutator \textit{rtd} \textit{idx})} & procedure & \pageref{records_s32} \\
\texttt{(record-predicate \textit{rtd})} & procedure & \pageref{records_s30} \\
\texttt{(record-rtd \textit{record})} & procedure & \pageref{records_s41} \\
\texttt{(record-type-descriptor \textit{record-name})} & syntax & \pageref{records_s28} \\
\texttt{(record-type-descriptor? \textit{obj})} & procedure & \pageref{records_s23} \\
\texttt{(record-type-field-names \textit{rtd})} & procedure & \pageref{records_s38} \\
\texttt{(record-type-generative? \textit{rtd})} & procedure & \pageref{records_s37} \\
\texttt{(record-type-name \textit{rtd})} & procedure & \pageref{records_s34} \\
\texttt{(record-type-opaque? \textit{rtd})} & procedure & \pageref{records_s37} \\
\texttt{(record-type-parent \textit{rtd})} & procedure & \pageref{records_s35} \\
\texttt{(record-type-sealed? \textit{rtd})} & procedure & \pageref{records_s37} \\
\texttt{(record-type-uid \textit{rtd})} & procedure & \pageref{records_s36} \\
\texttt{(record? \textit{obj})} & procedure & \pageref{records_s40} \\
\texttt{(remainder \textit{int\textsubscript{1}} \textit{int\textsubscript{2}})} & procedure & \pageref{objects_s98} \\
\texttt{(remove \textit{obj} \textit{list})} & procedure & \pageref{objects_s53} \\
\texttt{(remp \textit{procedure} \textit{list})} & procedure & \pageref{objects_s54} \\
\texttt{(remq \textit{obj} \textit{list})} & procedure & \pageref{objects_s53} \\
\texttt{(remv \textit{obj} \textit{list})} & procedure & \pageref{objects_s53} \\
\texttt{(reverse \textit{list})} & procedure & \pageref{objects_s50} \\
\texttt{(round \textit{real})} & procedure & \pageref{objects_s104} \\
\texttt{(scheme-report-environment \textit{version})} & procedure & \pageref{control_s82} \\
\texttt{sealed} & syntax & \pageref{records_s16} \\
\texttt{(serious-condition? \textit{obj})} & procedure & \pageref{exceptions_s19} \\
\texttt{(set! \textit{var} \textit{expr})} & syntax & \pageref{binding_s28} \\
\texttt{(set-car! \textit{pair} \textit{obj})} & procedure & \pageref{objects_s40} \\
\texttt{(set-cdr! \textit{pair} \textit{obj})} & procedure & \pageref{objects_s41} \\
\texttt{(set-port-position! \textit{port} \textit{pos})} & procedure & \pageref{io_s50} \\
\texttt{(simple-conditions \textit{condition})} & procedure & \pageref{exceptions_s16} \\
\texttt{(sin \textit{num})} & procedure & \pageref{objects_s131} \\
\texttt{(sint-list-\textgreater{}bytevector \textit{list} \textit{eness} \textit{size})} & procedure & \pageref{objects_s261} \\
\texttt{(sqrt \textit{num})} & procedure & \pageref{objects_s127} \\
\texttt{(standard-error-port)} & procedure & \pageref{io_s33} \\
\texttt{(standard-input-port)} & procedure & \pageref{io_s33} \\
\texttt{(standard-output-port)} & procedure & \pageref{io_s33} \\
\texttt{(string \textit{char} ...)} & procedure & \pageref{objects_s217} \\
\texttt{(string-\textgreater{}bytevector \textit{string} \textit{transcoder})} & procedure & \pageref{io_s92} \\
\texttt{(string-\textgreater{}list \textit{string})} & procedure & \pageref{objects_s228} \\
\texttt{(string-\textgreater{}number \textit{string})} & procedure & \pageref{objects_s147} \\
\texttt{(string-\textgreater{}number \textit{string} \textit{radix})} & procedure & \pageref{objects_s147} \\
\texttt{(string-\textgreater{}symbol \textit{string})} & procedure & \pageref{objects_s269} \\
\texttt{(string-\textgreater{}utf16 \textit{string})} & procedure & \pageref{io_s94} \\
\texttt{(string-\textgreater{}utf16 \textit{string} \textit{endianness})} & procedure & \pageref{io_s94} \\
\texttt{(string-\textgreater{}utf32 \textit{string})} & procedure & \pageref{io_s94} \\
\texttt{(string-\textgreater{}utf32 \textit{string} \textit{endianness})} & procedure & \pageref{io_s94} \\
\texttt{(string-\textgreater{}utf8 \textit{string})} & procedure & \pageref{io_s93} \\
\texttt{(string-append \textit{string} ...)} & procedure & \pageref{objects_s223} \\
\texttt{(string-ci-hash \textit{string})} & procedure & \pageref{objects_s279} \\
\texttt{(string-ci\textless{}=? \textit{string\textsubscript{1}} \textit{string\textsubscript{2}} \textit{string\textsubscript{3}} ...)} & procedure & \pageref{objects_s216} \\
\texttt{(string-ci\textless{}? \textit{string\textsubscript{1}} \textit{string\textsubscript{2}} \textit{string\textsubscript{3}} ...)} & procedure & \pageref{objects_s216} \\
\texttt{(string-ci=? \textit{string\textsubscript{1}} \textit{string\textsubscript{2}} \textit{string\textsubscript{3}} ...)} & procedure & \pageref{objects_s216} \\
\texttt{(string-ci\textgreater{}=? \textit{string\textsubscript{1}} \textit{string\textsubscript{2}} \textit{string\textsubscript{3}} ...)} & procedure & \pageref{objects_s216} \\
\texttt{(string-ci\textgreater{}? \textit{string\textsubscript{1}} \textit{string\textsubscript{2}} \textit{string\textsubscript{3}} ...)} & procedure & \pageref{objects_s216} \\
\texttt{(string-copy \textit{string})} & procedure & \pageref{objects_s222} \\
\texttt{(string-downcase \textit{string})} & procedure & \pageref{objects_s226} \\
\texttt{(string-fill! \textit{string} \textit{char})} & procedure & \pageref{objects_s225} \\
\texttt{(string-foldcase \textit{string})} & procedure & \pageref{objects_s226} \\
\texttt{(string-for-each \textit{procedure} \textit{string\textsubscript{1}} \textit{string\textsubscript{2}} ...)} & procedure & \pageref{control_s50} \\
\texttt{(string-hash \textit{string})} & procedure & \pageref{objects_s279} \\
\texttt{(string-length \textit{string})} & procedure & \pageref{objects_s219} \\
\texttt{(string-normalize-nfc \textit{string})} & procedure & \pageref{objects_s227} \\
\texttt{(string-normalize-nfd \textit{string})} & procedure & \pageref{objects_s227} \\
\texttt{(string-normalize-nfkc \textit{string})} & procedure & \pageref{objects_s227} \\
\texttt{(string-normalize-nfkd \textit{string})} & procedure & \pageref{objects_s227} \\
\texttt{(string-ref \textit{string} \textit{n})} & procedure & \pageref{objects_s220} \\
\texttt{(string-set! \textit{string} \textit{n} \textit{char})} & procedure & \pageref{objects_s221} \\
\texttt{(string-titlecase \textit{string})} & procedure & \pageref{objects_s226} \\
\texttt{(string-upcase \textit{string})} & procedure & \pageref{objects_s226} \\
\texttt{(string\textless{}=? \textit{string\textsubscript{1}} \textit{string\textsubscript{2}} \textit{string\textsubscript{3}} ...)} & procedure & \pageref{objects_s215} \\
\texttt{(string\textless{}? \textit{string\textsubscript{1}} \textit{string\textsubscript{2}} \textit{string\textsubscript{3}} ...)} & procedure & \pageref{objects_s215} \\
\texttt{(string=? \textit{string\textsubscript{1}} \textit{string\textsubscript{2}} \textit{string\textsubscript{3}} ...)} & procedure & \pageref{objects_s215} \\
\texttt{(string\textgreater{}=? \textit{string\textsubscript{1}} \textit{string\textsubscript{2}} \textit{string\textsubscript{3}} ...)} & procedure & \pageref{objects_s215} \\
\texttt{(string\textgreater{}? \textit{string\textsubscript{1}} \textit{string\textsubscript{2}} \textit{string\textsubscript{3}} ...)} & procedure & \pageref{objects_s215} \\
\texttt{(string? \textit{obj})} & procedure & \pageref{objects_s20} \\
\texttt{(substring \textit{string} \textit{start} \textit{end})} & procedure & \pageref{objects_s224} \\
\texttt{(symbol-\textgreater{}string \textit{symbol})} & procedure & \pageref{objects_s270} \\
\texttt{(symbol-hash \textit{symbol})} & procedure & \pageref{objects_s279} \\
\texttt{(symbol=? \textit{symbol\textsubscript{1}} \textit{symbol\textsubscript{2}})} & procedure & \pageref{objects_s268} \\
\texttt{(symbol? \textit{obj})} & procedure & \pageref{objects_s22} \\
\texttt{(syntax \textit{template})} & syntax & \pageref{syntax_s33} \\
\texttt{(syntax-\textgreater{}datum \textit{obj})} & procedure & \pageref{syntax_s44} \\
\texttt{(syntax-case \textit{expr} (\textit{literal} ...) \textit{clause} ...)} & syntax & \pageref{syntax_s30} \\
\texttt{(syntax-rules (\textit{literal} ...) \textit{clause} ...)} & syntax & \pageref{syntax_s14} \\
\texttt{(syntax-violation \textit{who} \textit{msg} \textit{form})} & procedure & \pageref{exceptions_s6} \\
\texttt{(syntax-violation \textit{who} \textit{msg} \textit{form} \textit{subform})} & procedure & \pageref{exceptions_s6} \\
\texttt{(syntax-violation-form \textit{condition})} & procedure & \pageref{exceptions_s30} \\
\texttt{(syntax-violation-subform \textit{condition})} & procedure & \pageref{exceptions_s30} \\
\texttt{(syntax-violation? \textit{obj})} & procedure & \pageref{exceptions_s30} \\
\texttt{(tan \textit{num})} & procedure & \pageref{objects_s131} \\
\texttt{(textual-port? \textit{obj})} & procedure & \pageref{io_s45} \\
\texttt{(transcoded-port \textit{binary-port} \textit{transcoder})} & procedure & \pageref{io_s47} \\
\texttt{(transcoder-codec \textit{transcoder})} & procedure & \pageref{io_s20} \\
\texttt{(transcoder-eol-style \textit{transcoder})} & procedure & \pageref{io_s20} \\
\texttt{(transcoder-error-handling-mode \textit{transcoder})} & procedure & \pageref{io_s20} \\
\texttt{(truncate \textit{real})} & procedure & \pageref{objects_s101} \\
\texttt{(u8-list-\textgreater{}bytevector \textit{list})} & procedure & \pageref{objects_s253} \\
\texttt{(uint-list-\textgreater{}bytevector \textit{list} \textit{eness} \textit{size})} & procedure & \pageref{objects_s261} \\
\texttt{(undefined-violation? \textit{obj})} & procedure & \pageref{exceptions_s31} \\
\texttt{(unless \textit{test-expr} \textit{expr\textsubscript{1}} \textit{expr\textsubscript{2}} ...)} & syntax & \pageref{control_s17} \\
\texttt{(unquote \textit{obj} ...)} & syntax & \pageref{objects_s5} \\
\texttt{(unquote-splicing \textit{obj} ...)} & syntax & \pageref{objects_s5} \\
\texttt{(unsyntax \textit{template} ...)} & syntax & \pageref{syntax_s40} \\
\texttt{(unsyntax-splicing \textit{template} ...)} & syntax & \pageref{syntax_s40} \\
\texttt{(utf-16-codec)} & procedure & \pageref{io_s22} \\
\texttt{(utf-8-codec)} & procedure & \pageref{io_s22} \\
\texttt{(utf16-\textgreater{}string \textit{bytevector} \textit{endianness})} & procedure & \pageref{io_s96} \\
\texttt{(utf16-\textgreater{}string \textit{bytevector} \textit{endianness} \textit{endianness-mandatory?})} & procedure & \pageref{io_s96} \\
\texttt{(utf32-\textgreater{}string \textit{bytevector} \textit{endianness})} & procedure & \pageref{io_s96} \\
\texttt{(utf32-\textgreater{}string \textit{bytevector} \textit{endianness} \textit{endianness-mandatory?})} & procedure & \pageref{io_s96} \\
\texttt{(utf8-\textgreater{}string \textit{bytevector})} & procedure & \pageref{io_s95} \\
\texttt{(values \textit{obj} ...)} & procedure & \pageref{control_s70} \\
\texttt{\textit{variable}} & syntax & \pageref{binding_s2} \\
\texttt{(vector \textit{obj} ...)} & procedure & \pageref{objects_s231} \\
\texttt{(vector-\textgreater{}list \textit{vector})} & procedure & \pageref{objects_s237} \\
\texttt{(vector-fill! \textit{vector} \textit{obj})} & procedure & \pageref{objects_s236} \\
\texttt{(vector-for-each \textit{procedure} \textit{vector\textsubscript{1}} \textit{vector\textsubscript{2}} ...)} & procedure & \pageref{control_s47} \\
\texttt{(vector-length \textit{vector})} & procedure & \pageref{objects_s233} \\
\texttt{(vector-map \textit{procedure} \textit{vector\textsubscript{1}} \textit{vector\textsubscript{1}} ...)} & procedure & \pageref{control_s44} \\
\texttt{(vector-ref \textit{vector} \textit{n})} & procedure & \pageref{objects_s234} \\
\texttt{(vector-set! \textit{vector} \textit{n} \textit{obj})} & procedure & \pageref{objects_s235} \\
\texttt{(vector-sort \textit{predicate} \textit{vector})} & procedure & \pageref{objects_s239} \\
\texttt{(vector-sort! \textit{predicate} \textit{vector})} & procedure & \pageref{objects_s239} \\
\texttt{(vector? \textit{obj})} & procedure & \pageref{objects_s21} \\
\texttt{(violation? \textit{obj})} & procedure & \pageref{exceptions_s20} \\
\texttt{(warning? \textit{obj})} & procedure & \pageref{exceptions_s23} \\
\texttt{(when \textit{test-expr} \textit{expr\textsubscript{1}} \textit{expr\textsubscript{2}} ...)} & syntax & \pageref{control_s17} \\
\texttt{(who-condition? \textit{obj})} & procedure & \pageref{exceptions_s26} \\
\texttt{(with-exception-handler \textit{procedure} \textit{thunk})} & procedure & \pageref{exceptions_s7} \\
\texttt{(with-input-from-file \textit{path} \textit{thunk})} & procedure & \pageref{io_s79} \\
\texttt{(with-output-to-file \textit{path} \textit{thunk})} & procedure & \pageref{io_s80} \\
\texttt{(with-syntax ((\textit{pattern} \textit{expr}) ...) \textit{body\textsubscript{1}} \textit{body\textsubscript{2}} ...)} & syntax & \pageref{syntax_s38} \\
\texttt{(write \textit{obj})} & procedure & \pageref{io_s84} \\
\texttt{(write \textit{obj} \textit{textual-output-port})} & procedure & \pageref{io_s84} \\
\texttt{(write-char \textit{char})} & procedure & \pageref{io_s86} \\
\texttt{(write-char \textit{char} \textit{textual-output-port})} & procedure & \pageref{io_s86} \\
\texttt{(zero? \textit{num})} & procedure & \pageref{objects_s93} \\
\end{longtabu}
