\SpecialChapter{Index}

\label{tspl_h0}




All page numbers appearing here refer to the printed version of this
book and also serve as hypertext links to the corresponding locations
in the electronic version of this book.


   
{\footnotesize
\begin{multicols}{2}
\RaggedRight
\texttt{!} (exclamation point), \pageref{intro_s50}
  
\texttt{"} (double quote), \pageref{objects_s213}
  
\texttt{\#{}!r6rs}, \pageref{grammar_s12}
  
\texttt{\#{}'} (\texttt{syntax}), \textit{\pageref{syntax_s33}}
  
\texttt{\#{},} (\texttt{unsyntax}), \textit{\pageref{syntax_s40}}
  
\texttt{\#{},\@{}} (\texttt{unsyntax-splicing}), \textit{\pageref{syntax_s40}}
  
\texttt{\#{};} (datum comment), \pageref{grammar_s8}
  
\texttt{\#{}\textbackslash{}}, \pageref{objects_s200}
  
\texttt{\#{}`} (\texttt{quasisyntax}), \textit{\pageref{syntax_s40}}
  
\texttt{\#{}\textbar{}...\textbar{}\#{}} (block comment), \pageref{grammar_s10}
  
\texttt{\#{}b} (binary), \pageref{objects_s78}
  
\texttt{\#{}d} (decimal), \pageref{objects_s80}
  
\texttt{\#{}f}, \pageref{intro_s39}, \pageref{start_s105}, \pageref{objects_s8}
  
\texttt{\#{}o} (octal), \pageref{objects_s79}
  
\texttt{\#{}t}, \pageref{intro_s38}, \pageref{start_s104}, \pageref{objects_s7}
  
\texttt{\#{}x} (hexadecimal), \pageref{objects_s81}
  
\texttt{\&{}assertion}, \textit{\pageref{exceptions_s21}}
  
\texttt{\&{}condition}, \textit{\pageref{exceptions_s13}}
  
\texttt{\&{}error}, \textit{\pageref{exceptions_s22}}
  
\texttt{\&{}i/o}, \textit{\pageref{exceptions_s32}}
  
\texttt{\&{}i/o-decoding}, \textit{\pageref{exceptions_s42}}
  
\texttt{\&{}i/o-encoding}, \textit{\pageref{exceptions_s43}}
  
\texttt{\&{}i/o-file-already-exists}, \textit{\pageref{exceptions_s39}}
  
\texttt{\&{}i/o-file-does-not-exist}, \textit{\pageref{exceptions_s40}}
  
\texttt{\&{}i/o-file-is-read-only}, \textit{\pageref{exceptions_s38}}
  
\texttt{\&{}i/o-file-protection}, \textit{\pageref{exceptions_s37}}
  
\texttt{\&{}i/o-filename}, \textit{\pageref{exceptions_s36}}
  
\texttt{\&{}i/o-invalid-position}, \textit{\pageref{exceptions_s35}}
  
\texttt{\&{}i/o-port}, \textit{\pageref{exceptions_s41}}
  
\texttt{\&{}i/o-read}, \textit{\pageref{exceptions_s33}}
  
\texttt{\&{}i/o-write}, \textit{\pageref{exceptions_s34}}
  
\texttt{\&{}implementation-restriction}, \textit{\pageref{exceptions_s28}}
  
\texttt{\&{}irritants}, \textit{\pageref{exceptions_s25}}
  
\texttt{\&{}lexical}, \textit{\pageref{exceptions_s29}}
  
\texttt{\&{}message}, \textit{\pageref{exceptions_s24}}
  
\texttt{\&{}no-infinities}, \textit{\pageref{exceptions_s44}}
  
\texttt{\&{}no-nans}, \textit{\pageref{exceptions_s45}}
  
\texttt{\&{}non-continuable}, \textit{\pageref{exceptions_s27}}
  
\texttt{\&{}serious}, \textit{\pageref{exceptions_s19}}
  
\texttt{\&{}syntax}, \textit{\pageref{exceptions_s30}}
  
\texttt{\&{}undefined}, \textit{\pageref{exceptions_s31}}
  
\texttt{\&{}violation}, \textit{\pageref{exceptions_s20}}
  
\texttt{\&{}warning}, \textit{\pageref{exceptions_s23}}
  
\texttt{\&{}who}, \textit{\pageref{exceptions_s26}}
  
\texttt{'} (\texttt{quote}), \pageref{start_s15}, \pageref{start_s44}, \pageref{further_s4}, \textit{\pageref{objects_s2}}
  
\texttt{()}, \pageref{intro_s33}, \pageref{start_s23}
  
\texttt{*}, \pageref{start_s8}, \textit{\pageref{objects_s91}}
  
\texttt{+}, \pageref{start_s6}, \textit{\pageref{objects_s89}}
  
\texttt{,} (\texttt{unquote}), \textit{\pageref{objects_s5}}
  
\texttt{,\@{}} (\texttt{unquote-splicing}), \textit{\pageref{objects_s5}}
  
\texttt{-}, \pageref{start_s7}, \textit{\pageref{objects_s90}}
  
\texttt{-\textgreater{}}, \pageref{intro_s49}
  
\texttt{.} (dot), \pageref{start_s30}, \pageref{grammar_s20}
  
\texttt{...} (ellipsis), \pageref{further_s20}, \pageref{syntax_s20}, \textit{\pageref{syntax_s26}}
  
\texttt{/}, \pageref{start_s9}, \textit{\pageref{objects_s92}}
  
\texttt{;} (comment), \pageref{intro_s43}, \pageref{grammar_s6}
  
\texttt{\textless{}}, \textit{\pageref{objects_s88}}
  
\texttt{\textless{}=}, \textit{\pageref{objects_s88}}
  
\texttt{=}, \textit{\pageref{objects_s88}}
  
\texttt{=\textgreater{}}, \pageref{control_s14}, \textit{\pageref{control_s16}}
  
\texttt{\textgreater{}}, \textit{\pageref{objects_s88}}
  
\texttt{\textgreater{}=}, \textit{\pageref{objects_s88}}
  
\texttt{?} (question mark), \pageref{intro_s46}, \pageref{start_s111}
  
\texttt{\_{}} (underscore), \pageref{further_s18}, \pageref{syntax_s25}, \pageref{syntax_s59}
  
\texttt{\_{}} (underscore), \pageref{syntax_s18}, \textit{\pageref{syntax_s26}}
  
\texttt{`} (\texttt{quasiquote}), \textit{\pageref{objects_s5}}
  
\texttt{abs}, \pageref{start_s98}, \textit{\pageref{objects_s105}}, \pageref{objects_s126}
  
abstract objects, \pageref{start_s179}, \pageref{examples_s60}
  
\texttt{acos}, \textit{\pageref{objects_s132}}
  
actual parameters, \pageref{start_s64}, \pageref{binding_s7}
  
Algol 60, \pageref{intro_s27}
  
\texttt{and}, \pageref{start_s108}, \pageref{further_s22}, \textit{\pageref{control_s11}}
  
\texttt{angle}, \textit{\pageref{objects_s124}}
  
\texttt{append}, \pageref{start_s151}, \textit{\pageref{objects_s49}}
  
\texttt{apply}, \textit{\pageref{control_s3}}
  
arbitrary precision, \pageref{objects_s76}
  
\texttt{asin}, \textit{\pageref{objects_s132}}
  
\texttt{assert}, \textit{\pageref{exceptions_s5}}
  
\texttt{assertion-violation}, \textit{\pageref{exceptions_s4}}
  
\texttt{assertion-violation?}, \textit{\pageref{exceptions_s21}}
  
assignment, \pageref{binding_s29}
  
assignments, \pageref{start_s163}, \pageref{binding_s30}
  
\texttt{assoc}, \textit{\pageref{objects_s58}}
  
association list, \pageref{objects_s59}, \pageref{objects_s61}, \pageref{objects_s273}, \pageref{examples_s50}
  
\texttt{assp}, \textit{\pageref{objects_s60}}
  
\texttt{assq}, \textit{\pageref{objects_s58}}
  
\texttt{assv}, \textit{\pageref{objects_s58}}
  
\texttt{atan}, \textit{\pageref{objects_s133}}
  
\texttt{atom?}, \pageref{start_s127}
  
auxiliary keywords, \pageref{further_s16}, \pageref{syntax_s22}
  
base case, \pageref{start_s134}
  
\texttt{be-like-begin}, \pageref{syntax_s54}
  
\texttt{begin}, \pageref{start_s174}, \pageref{further_s10}, \pageref{binding_s26}, \textit{\pageref{control_s4}}
  
binary port, \pageref{io_s6}
  
binary trees, \pageref{objects_s33}
  
\texttt{binary-port?}, \textit{\pageref{io_s45}}
  
binding, \pageref{intro_s14}
  
\texttt{bitwise-and}, \textit{\pageref{objects_s134}}
  
\texttt{bitwise-arithmetic-shift}, \textit{\pageref{objects_s144}}
  
\texttt{bitwise-arithmetic-shift-left}, \textit{\pageref{objects_s143}}
  
\texttt{bitwise-arithmetic-shift-right}, \textit{\pageref{objects_s143}}
  
\texttt{bitwise-bit-count}, \textit{\pageref{objects_s136}}
  
\texttt{bitwise-bit-field}, \textit{\pageref{objects_s141}}
  
\texttt{bitwise-bit-set?}, \textit{\pageref{objects_s139}}
  
\texttt{bitwise-copy-bit}, \textit{\pageref{objects_s140}}
  
\texttt{bitwise-copy-bit-field}, \textit{\pageref{objects_s142}}
  
\texttt{bitwise-first-bit-set}, \textit{\pageref{objects_s138}}
  
\texttt{bitwise-if}, \textit{\pageref{objects_s135}}
  
\texttt{bitwise-ior}, \textit{\pageref{objects_s134}}
  
\texttt{bitwise-length}, \textit{\pageref{objects_s137}}
  
\texttt{bitwise-not}, \textit{\pageref{objects_s134}}
  
\texttt{bitwise-reverse-bit-field}, \textit{\pageref{objects_s146}}
  
\texttt{bitwise-rotate-bit-field}, \textit{\pageref{objects_s145}}
  
\texttt{bitwise-xor}, \textit{\pageref{objects_s134}}
  
block buffering, \pageref{io_s17}
  
block comment ( \texttt{\#{}\textbar{}...\textbar{}\#{}} ), \pageref{grammar_s11}
  
block structure, \pageref{intro_s13}
  
boolean syntax, \pageref{grammar_s14}
  
boolean values, \pageref{intro_s35}
  
\texttt{boolean=?}, \textit{\pageref{objects_s271}}
  
\texttt{boolean?}, \textit{\pageref{objects_s14}}
  
\texttt{bound-identifier=?}, \textit{\pageref{syntax_s37}}
  
brackets ( \texttt{[} \texttt{]} ), \pageref{intro_s34}, \pageref{objects_s34}
  
\texttt{break}, \pageref{syntax_s47}
  
buffer modes, \pageref{io_s16}
  
\texttt{buffer-mode}, \textit{\pageref{io_s27}}
  
\texttt{buffer-mode?}, \textit{\pageref{io_s28}}
  
bytevector syntax, \pageref{grammar_s23}
  
\texttt{bytevector-\textgreater{}sint-list}, \textit{\pageref{objects_s260}}
  
\texttt{bytevector-\textgreater{}string}, \textit{\pageref{io_s91}}
  
\texttt{bytevector-\textgreater{}u8-list}, \textit{\pageref{objects_s252}}
  
\texttt{bytevector-\textgreater{}uint-list}, \textit{\pageref{objects_s260}}
  
\texttt{bytevector-copy}, \textit{\pageref{objects_s246}}
  
\texttt{bytevector-copy!}, \textit{\pageref{objects_s247}}
  
\texttt{bytevector-fill!}, \textit{\pageref{objects_s245}}
  
\texttt{bytevector-ieee-double-native-ref}, \textit{\pageref{objects_s262}}
  
\texttt{bytevector-ieee-double-native-set!}, \textit{\pageref{objects_s263}}
  
\texttt{bytevector-ieee-double-ref}, \textit{\pageref{objects_s264}}
  
\texttt{bytevector-ieee-double-set!}, \textit{\pageref{objects_s265}}
  
\texttt{bytevector-ieee-single-native-ref}, \textit{\pageref{objects_s262}}
  
\texttt{bytevector-ieee-single-native-set!}, \textit{\pageref{objects_s263}}
  
\texttt{bytevector-ieee-single-ref}, \textit{\pageref{objects_s264}}
  
\texttt{bytevector-ieee-single-set!}, \textit{\pageref{objects_s265}}
  
\texttt{bytevector-length}, \textit{\pageref{objects_s243}}
  
\texttt{bytevector-s16-native-ref}, \textit{\pageref{objects_s254}}
  
\texttt{bytevector-s16-native-set!}, \textit{\pageref{objects_s255}}
  
\texttt{bytevector-s16-ref}, \textit{\pageref{objects_s256}}
  
\texttt{bytevector-s16-set!}, \textit{\pageref{objects_s257}}
  
\texttt{bytevector-s32-native-ref}, \textit{\pageref{objects_s254}}
  
\texttt{bytevector-s32-native-set!}, \textit{\pageref{objects_s255}}
  
\texttt{bytevector-s32-ref}, \textit{\pageref{objects_s256}}
  
\texttt{bytevector-s32-set!}, \textit{\pageref{objects_s257}}
  
\texttt{bytevector-s64-native-ref}, \textit{\pageref{objects_s254}}
  
\texttt{bytevector-s64-native-set!}, \textit{\pageref{objects_s255}}
  
\texttt{bytevector-s64-ref}, \textit{\pageref{objects_s256}}
  
\texttt{bytevector-s64-set!}, \textit{\pageref{objects_s257}}
  
\texttt{bytevector-s8-ref}, \textit{\pageref{objects_s249}}
  
\texttt{bytevector-s8-set!}, \textit{\pageref{objects_s251}}
  
\texttt{bytevector-sint-ref}, \textit{\pageref{objects_s258}}
  
\texttt{bytevector-sint-set!}, \textit{\pageref{objects_s259}}
  
\texttt{bytevector-u16-native-ref}, \textit{\pageref{objects_s254}}
  
\texttt{bytevector-u16-native-set!}, \textit{\pageref{objects_s255}}
  
\texttt{bytevector-u16-ref}, \textit{\pageref{objects_s256}}
  
\texttt{bytevector-u16-set!}, \textit{\pageref{objects_s257}}
  
\texttt{bytevector-u32-native-ref}, \textit{\pageref{objects_s254}}
  
\texttt{bytevector-u32-native-set!}, \textit{\pageref{objects_s255}}
  
\texttt{bytevector-u32-ref}, \textit{\pageref{objects_s256}}
  
\texttt{bytevector-u32-set!}, \textit{\pageref{objects_s257}}
  
\texttt{bytevector-u64-native-ref}, \textit{\pageref{objects_s254}}
  
\texttt{bytevector-u64-native-set!}, \textit{\pageref{objects_s255}}
  
\texttt{bytevector-u64-ref}, \textit{\pageref{objects_s256}}
  
\texttt{bytevector-u64-set!}, \textit{\pageref{objects_s257}}
  
\texttt{bytevector-u8-ref}, \textit{\pageref{objects_s248}}
  
\texttt{bytevector-u8-set!}, \textit{\pageref{objects_s250}}
  
\texttt{bytevector-uint-ref}, \textit{\pageref{objects_s258}}
  
\texttt{bytevector-uint-set!}, \textit{\pageref{objects_s259}}
  
\texttt{bytevector=?}, \textit{\pageref{objects_s244}}
  
\texttt{bytevector?}, \textit{\pageref{objects_s24}}
  
C, \pageref{examples_s23}
  
\texttt{caaaar}, \textit{\pageref{objects_s42}}
  
\texttt{caaadr}, \textit{\pageref{objects_s42}}
  
\texttt{caaar}, \textit{\pageref{objects_s42}}
  
\texttt{caadar}, \textit{\pageref{objects_s42}}
  
\texttt{caaddr}, \textit{\pageref{objects_s42}}
  
\texttt{caadr}, \textit{\pageref{objects_s42}}
  
\texttt{caar}, \textit{\pageref{objects_s42}}
  
\texttt{caar, cadr, ..., cddddr}, \pageref{start_s97}
  
\texttt{cadaar}, \textit{\pageref{objects_s42}}
  
\texttt{cadadr}, \textit{\pageref{objects_s42}}
  
\texttt{cadar}, \textit{\pageref{objects_s42}}
  
\texttt{caddar}, \textit{\pageref{objects_s42}}
  
\texttt{cadddr}, \textit{\pageref{objects_s42}}
  
\texttt{caddr}, \textit{\pageref{objects_s42}}
  
\texttt{cadr}, \pageref{start_s83}, \pageref{start_s85}, \pageref{start_s93}, \textit{\pageref{objects_s42}}
  
call-by-name, \pageref{examples_s58}
  
call-by-value, \pageref{examples_s57}
  
\texttt{call-with-bytevector-output-port}, \textit{\pageref{io_s38}}
  
\texttt{call-with-current-continuation}, \textit{\pageref{control_s54}}, \pageref{examples_s99}
  
\texttt{call-with-input-file}, \textit{\pageref{io_s77}}
  
\texttt{call-with-output-file}, \textit{\pageref{io_s78}}
  
\texttt{call-with-port}, \textit{\pageref{io_s51}}
  
\texttt{call-with-string-output-port}, \textit{\pageref{io_s39}}
  
\texttt{call-with-values}, \pageref{control_s69}, \textit{\pageref{control_s71}}
  
\texttt{call/cc}, \pageref{further_s62}, \pageref{control_s53}, \textit{\pageref{control_s54}}, \pageref{control_s62}, \pageref{control_s77}, \pageref{examples_s98}, \pageref{examples_s100}
  
\texttt{car}, \pageref{start_s21}, \pageref{objects_s30}, \textit{\pageref{objects_s38}}
  
\texttt{case}, \pageref{start_s189}, \textit{\pageref{control_s18}}, \pageref{syntax_s41}
  
\texttt{case-lambda}, \textit{\pageref{binding_s13}}
  
\texttt{cdaaar}, \textit{\pageref{objects_s42}}
  
\texttt{cdaadr}, \textit{\pageref{objects_s42}}
  
\texttt{cdaar}, \textit{\pageref{objects_s42}}
  
\texttt{cdadar}, \textit{\pageref{objects_s42}}
  
\texttt{cdaddr}, \textit{\pageref{objects_s42}}
  
\texttt{cdadr}, \textit{\pageref{objects_s42}}
  
\texttt{cdar}, \textit{\pageref{objects_s42}}
  
\texttt{cddaar}, \textit{\pageref{objects_s42}}
  
\texttt{cddadr}, \textit{\pageref{objects_s42}}
  
\texttt{cddar}, \textit{\pageref{objects_s42}}
  
\texttt{cdddar}, \textit{\pageref{objects_s42}}
  
\texttt{cddddr}, \textit{\pageref{objects_s42}}
  
\texttt{cdddr}, \textit{\pageref{objects_s42}}
  
\texttt{cddr}, \pageref{start_s84}, \pageref{start_s94}, \textit{\pageref{objects_s42}}
  
\texttt{cdr}, \pageref{start_s22}, \pageref{start_s114}, \pageref{objects_s29}, \textit{\pageref{objects_s39}}
  
\texttt{ceiling}, \textit{\pageref{objects_s103}}
  
\texttt{char-\textgreater{}integer}, \textit{\pageref{objects_s210}}
  
\texttt{char-alphabetic?}, \textit{\pageref{objects_s203}}
  
\texttt{char-ci\textless{}=?}, \textit{\pageref{objects_s202}}
  
\texttt{char-ci\textless{}?}, \textit{\pageref{objects_s202}}
  
\texttt{char-ci=?}, \textit{\pageref{objects_s202}}
  
\texttt{char-ci\textgreater{}=?}, \textit{\pageref{objects_s202}}
  
\texttt{char-ci\textgreater{}?}, \textit{\pageref{objects_s202}}
  
\texttt{char-downcase}, \textit{\pageref{objects_s207}}
  
\texttt{char-foldcase}, \textit{\pageref{objects_s209}}
  
\texttt{char-general-category}, \textit{\pageref{objects_s205}}
  
\texttt{char-lower-case?}, \textit{\pageref{objects_s204}}
  
\texttt{char-numeric?}, \textit{\pageref{objects_s203}}
  
\texttt{char-title-case?}, \textit{\pageref{objects_s204}}
  
\texttt{char-titlecase}, \textit{\pageref{objects_s208}}
  
\texttt{char-upcase}, \textit{\pageref{objects_s206}}
  
\texttt{char-upper-case?}, \textit{\pageref{objects_s204}}
  
\texttt{char-whitespace?}, \textit{\pageref{objects_s203}}
  
\texttt{char\textless{}=?}, \textit{\pageref{objects_s201}}
  
\texttt{char\textless{}?}, \textit{\pageref{objects_s201}}
  
\texttt{char=?}, \textit{\pageref{objects_s201}}
  
\texttt{char\textgreater{}=?}, \textit{\pageref{objects_s201}}
  
\texttt{char\textgreater{}?}, \textit{\pageref{objects_s201}}
  
\texttt{char?}, \textit{\pageref{objects_s19}}
  
character syntax, \pageref{grammar_s15}
  
characters, \pageref{objects_s199}
  
Chez Scheme, \pageref{preface_s3}, \pageref{start_s139}
  
child type, \pageref{records_s10}
  
circular lists, \pageref{objects_s36}
  
\texttt{close-input-port}, \textit{\pageref{io_s88}}
  
\texttt{close-output-port}, \textit{\pageref{io_s88}}
  
\texttt{close-port}, \textit{\pageref{io_s46}}
  
codec, \pageref{io_s10}
  
\texttt{command-line}, \textit{\pageref{libraries_s17}}
  
comments, \pageref{intro_s42}, \pageref{grammar_s5}
  
Common Lisp, \pageref{intro_s28}
  
compiler, \pageref{intro_s9}
  
\textit{complete}, \textit{see} engines
  
complex numbers, \pageref{objects_s67}, \pageref{examples_s69}
  
\texttt{complex?}, \textit{\pageref{objects_s17}}, \pageref{objects_s71}
  
\texttt{compose}, \pageref{start_s95}
  
compound condition, \pageref{exceptions_s11}
  
\texttt{cond}, \pageref{start_s124}, \pageref{start_s142}, \textit{\pageref{control_s13}}, \pageref{syntax_s39}
  
\texttt{condition}, \textit{\pageref{exceptions_s15}}
  
condition object, \pageref{exceptions_s9}
  
condition type, \pageref{exceptions_s10}
  
\texttt{condition-accessor}, \textit{\pageref{exceptions_s18}}
  
\texttt{condition-irritants}, \textit{\pageref{exceptions_s25}}
  
\texttt{condition-message}, \textit{\pageref{exceptions_s24}}
  
\texttt{condition-predicate}, \textit{\pageref{exceptions_s18}}
  
\texttt{condition-who}, \textit{\pageref{exceptions_s26}}
  
\texttt{condition?}, \textit{\pageref{exceptions_s14}}
  
conditionals, \pageref{control_s9}
  
conditions, \pageref{exceptions_s1}
  
\texttt{cons}, \pageref{start_s25}, \textit{\pageref{objects_s37}}
  
cons cell, \pageref{objects_s27}
  
\texttt{cons*}, \textit{\pageref{objects_s44}}
  
consing, \pageref{start_s26}
  
constant, \textit{\pageref{objects_s1}}
  
constants, \pageref{start_s42}, \pageref{objects_s4}
  
continuation-passing style, \pageref{further_s71}, \pageref{examples_s77}
  
continuations, \pageref{intro_s24}, \pageref{further_s61}, \pageref{control_s57}, \pageref{examples_s88}
  
control structures, \pageref{control_s0}
  
core syntactic forms, \pageref{intro_s6}, \pageref{start_s47}, \pageref{further_s0}, \pageref{examples_s51}
  
\texttt{cos}, \textit{\pageref{objects_s131}}
  
CPS, \pageref{further_s72}
  
current exception handler, \pageref{exceptions_s2}
  
\texttt{current-error-port}, \textit{\pageref{io_s32}}
  
\texttt{current-input-port}, \textit{\pageref{io_s32}}
  
\texttt{current-output-port}, \textit{\pageref{io_s32}}
  
cyclic lists, \pageref{start_s198}
  
\texttt{d} (double), \pageref{objects_s84}
  
data, \pageref{objects_s3}
  
datum comment ( \texttt{\#{};} ), \pageref{grammar_s9}
  
datum syntax, \pageref{grammar_s0}, \pageref{grammar_s13}
  
\texttt{datum-\textgreater{}syntax}, \textit{\pageref{syntax_s45}}, \pageref{syntax_s65}, \pageref{syntax_s71}
  
default protocol, \pageref{records_s12}
  
\texttt{define}, \pageref{start_s78}, \pageref{further_s80}, \textit{\pageref{binding_s24}}
  
\texttt{define-condition-type}, \textit{\pageref{exceptions_s17}}
  
\texttt{define-enumeration}, \textit{\pageref{objects_s290}}
  
\texttt{define-integrable}, \pageref{syntax_s61}
  
\texttt{define-object}, \pageref{examples_s63}
  
\texttt{define-record-type}, \pageref{records_s1}, \textit{\pageref{records_s13}}
  
\texttt{define-structure}, \pageref{syntax_s70}
  
\texttt{define-syntax}, \pageref{further_s13}, \pageref{syntax_s3}, \textit{\pageref{syntax_s12}}, \pageref{examples_s17}
  
defining syntactic extensions, \pageref{further_s11}
  
defun syntax, \pageref{start_s87}, \pageref{further_s9}
  
\texttt{delay}, \textit{\pageref{control_s65}}
  
delayed evaluation, \pageref{examples_s59}
  
\texttt{delete-file}, \textit{\pageref{io_s90}}
  
\texttt{delq!}, \pageref{start_s185}
  
\texttt{denominator}, \textit{\pageref{objects_s119}}
  
\texttt{describe-segment}, \pageref{control_s75}
  
\texttt{display}, \textit{\pageref{io_s85}}, \pageref{examples_s33}
  
\texttt{div}, \textit{\pageref{objects_s99}}
  
\texttt{div-and-mod}, \textit{\pageref{objects_s99}}
  
\texttt{div0}, \textit{\pageref{objects_s100}}
  
\texttt{div0-and-mod0}, \textit{\pageref{objects_s100}}
  
\texttt{divisors}, \pageref{control_s24}, \pageref{control_s29}
  
\texttt{do}, \textit{\pageref{control_s25}}, \pageref{syntax_s53}
  
dot ( \texttt{.} ), \pageref{start_s31}, \pageref{grammar_s21}
  
dotted pair, \pageref{start_s32}, \pageref{objects_s35}
  
\texttt{double}, \pageref{start_s65}, \pageref{start_s89}
  
double quotes, \pageref{objects_s214}
  
\texttt{double-any}, \pageref{start_s79}
  
\texttt{double-cons}, \pageref{start_s66}, \pageref{start_s90}
  
\texttt{doubler}, \pageref{start_s88}
  
doubly recursive, \pageref{further_s49}
  
\texttt{dxdy}, \pageref{control_s72}
  
dynamic allocation, \pageref{intro_s2}
  
\texttt{dynamic-wind}, \textit{\pageref{control_s56}}
  
ellipsis ( \texttt{...} ), \pageref{further_s21}, \pageref{syntax_s21}
  
\texttt{else}, \pageref{control_s15}, \textit{\pageref{control_s16}}, \pageref{control_s19}
  
empty list, \pageref{intro_s32}, \pageref{start_s24}
  
\texttt{endianness}, \textit{\pageref{objects_s240}}
  
engines, \pageref{examples_s82}
  
\texttt{enum-set-\textgreater{}list}, \textit{\pageref{objects_s294}}
  
\texttt{enum-set-complement}, \textit{\pageref{objects_s299}}
  
\texttt{enum-set-constructor}, \textit{\pageref{objects_s292}}
  
\texttt{enum-set-difference}, \textit{\pageref{objects_s298}}
  
\texttt{enum-set-indexer}, \textit{\pageref{objects_s301}}
  
\texttt{enum-set-intersection}, \textit{\pageref{objects_s298}}
  
\texttt{enum-set-member?}, \textit{\pageref{objects_s297}}
  
\texttt{enum-set-projection}, \textit{\pageref{objects_s300}}
  
\texttt{enum-set-subset?}, \textit{\pageref{objects_s295}}
  
\texttt{enum-set-union}, \textit{\pageref{objects_s298}}
  
\texttt{enum-set-universe}, \textit{\pageref{objects_s293}}
  
\texttt{enum-set=?}, \textit{\pageref{objects_s296}}
  
\texttt{environment}, \textit{\pageref{control_s81}}
  
environment, \pageref{examples_s49}
  
eof object, \pageref{io_s4}
  
\texttt{eof-object}, \textit{\pageref{io_s54}}
  
\texttt{eof-object?}, \pageref{io_s5}, \textit{\pageref{io_s53}}
  
eol style, \pageref{io_s14}
  
\texttt{eol-style}, \textit{\pageref{io_s23}}
  
\texttt{eq?}, \textit{\pageref{objects_s10}}
  
\texttt{equal-hash}, \textit{\pageref{objects_s279}}
  
\texttt{equal?}, \textit{\pageref{objects_s13}}
  
equivalence predicates, \pageref{objects_s9}
  
\texttt{eqv?}, \pageref{start_s116}, \textit{\pageref{objects_s12}}
  
\texttt{error}, \textit{\pageref{exceptions_s4}}
  
error handling mode, \pageref{io_s15}
  
\texttt{error-handling-mode}, \textit{\pageref{io_s25}}
  
\texttt{error?}, \textit{\pageref{exceptions_s22}}
  
\texttt{eval}, \textit{\pageref{control_s80}}
  
\texttt{even?}, \pageref{start_s160}, \pageref{further_s37}, \pageref{further_s82}, \textit{\pageref{objects_s96}}
  
\texttt{exact}, \textit{\pageref{objects_s114}}
  
\texttt{exact-\textgreater{}inexact}, \textit{\pageref{objects_s116}}
  
\texttt{exact-integer-sqrt}, \textit{\pageref{objects_s128}}
  
\texttt{exact?}, \pageref{objects_s73}, \textit{\pageref{objects_s86}}
  
exactness, \pageref{objects_s72}, \pageref{objects_s113}
  
exactness preserving, \pageref{objects_s75}
  
\texttt{except} import set, \pageref{libraries_s10}
  
exceptions, \pageref{intro_s55}, \pageref{exceptions_s0}
  
exclamation point ( \texttt{!} ), \pageref{intro_s51}
  
\texttt{exists}, \textit{\pageref{control_s36}}
  
\texttt{exit}, \textit{\pageref{libraries_s18}}
  
\texttt{exp}, \textit{\pageref{objects_s129}}
  
expansion, \pageref{further_s3}
  
\textit{expire}, \textit{see} engines
  
\texttt{export}, \pageref{libraries_s3}
  
export level, \pageref{libraries_s7}
  
expressions, \pageref{intro_s40}
  
\texttt{expt}, \textit{\pageref{objects_s111}}
  
extended examples, \pageref{examples_s0}
  
\texttt{f} (single), \pageref{objects_s83}
  
\texttt{factor}, \pageref{further_s51}, \pageref{further_s54}, \pageref{further_s60}
  
\texttt{factorial}, \pageref{further_s46}, \pageref{further_s64}, \pageref{control_s27}
  
false, \pageref{intro_s37}, \pageref{start_s107}
  
fast Fourier transform (FFT), \pageref{examples_s70}
  
fenders, \pageref{syntax_s31}, \pageref{syntax_s36}
  
\texttt{fibonacci}, \pageref{further_s47}, \pageref{binding_s33}, \pageref{control_s28}, \pageref{examples_s92}
  
Fibonacci numbers, \pageref{further_s48}, \pageref{binding_s32}
  
\texttt{fields}, \textit{\pageref{records_s16}}
  
file, \pageref{io_s3}
  
\texttt{file-exists?}, \textit{\pageref{io_s89}}
  
\texttt{file-options}, \textit{\pageref{io_s26}}
  
\texttt{filter}, \textit{\pageref{objects_s55}}
  
\texttt{find}, \textit{\pageref{objects_s57}}
  
\texttt{finite?}, \textit{\pageref{objects_s97}}
  
first-class data values, \pageref{intro_s4}
  
first-class procedures, \pageref{intro_s18}
  
fixnum, \pageref{objects_s149}
  
\texttt{fixnum-\textgreater{}flonum}, \textit{\pageref{objects_s198}}
  
\texttt{fixnum-width}, \textit{\pageref{objects_s152}}
  
\texttt{fixnum?}, \textit{\pageref{objects_s150}}
  
\texttt{fl*}, \textit{\pageref{objects_s186}}
  
\texttt{fl+}, \textit{\pageref{objects_s184}}
  
\texttt{fl-}, \textit{\pageref{objects_s185}}
  
\texttt{fl/}, \textit{\pageref{objects_s187}}
  
\texttt{fl\textless{}=?}, \textit{\pageref{objects_s178}}
  
\texttt{fl\textless{}?}, \textit{\pageref{objects_s178}}
  
\texttt{fl=?}, \textit{\pageref{objects_s178}}
  
\texttt{fl\textgreater{}=?}, \textit{\pageref{objects_s178}}
  
\texttt{fl\textgreater{}?}, \textit{\pageref{objects_s178}}
  
\texttt{flabs}, \textit{\pageref{objects_s192}}
  
\texttt{flacos}, \textit{\pageref{objects_s195}}
  
\texttt{flasin}, \textit{\pageref{objects_s195}}
  
\texttt{flatan}, \textit{\pageref{objects_s195}}
  
\texttt{flceiling}, \textit{\pageref{objects_s190}}
  
\texttt{flcos}, \textit{\pageref{objects_s194}}
  
\texttt{fldenominator}, \textit{\pageref{objects_s191}}
  
\texttt{fldiv}, \textit{\pageref{objects_s188}}
  
\texttt{fldiv-and-mod}, \textit{\pageref{objects_s188}}
  
\texttt{fldiv0}, \textit{\pageref{objects_s189}}
  
\texttt{fldiv0-and-mod0}, \textit{\pageref{objects_s189}}
  
\texttt{fleven?}, \textit{\pageref{objects_s182}}
  
\texttt{flexp}, \textit{\pageref{objects_s193}}
  
\texttt{flexpt}, \textit{\pageref{objects_s197}}
  
\texttt{flfinite?}, \textit{\pageref{objects_s181}}
  
\texttt{flfloor}, \textit{\pageref{objects_s190}}
  
\texttt{flinfinite?}, \textit{\pageref{objects_s181}}
  
\texttt{flinteger?}, \textit{\pageref{objects_s180}}
  
\texttt{flip-flop}, \pageref{binding_s31}
  
\texttt{fllog}, \textit{\pageref{objects_s193}}
  
\texttt{flmax}, \textit{\pageref{objects_s183}}
  
\texttt{flmin}, \textit{\pageref{objects_s183}}
  
\texttt{flmod}, \textit{\pageref{objects_s188}}
  
\texttt{flmod0}, \textit{\pageref{objects_s189}}
  
\texttt{flnan?}, \textit{\pageref{objects_s181}}
  
\texttt{flnegative?}, \textit{\pageref{objects_s179}}
  
\texttt{flnumerator}, \textit{\pageref{objects_s191}}
  
floating
point, \pageref{objects_s77}
  
\texttt{flodd?}, \textit{\pageref{objects_s182}}
  
flonum, \pageref{objects_s176}
  
\texttt{flonum?}, \textit{\pageref{objects_s177}}
  
\texttt{floor}, \textit{\pageref{objects_s102}}
  
\texttt{flpositive?}, \textit{\pageref{objects_s179}}
  
\texttt{flround}, \textit{\pageref{objects_s190}}
  
\texttt{flsin}, \textit{\pageref{objects_s194}}
  
\texttt{flsqrt}, \textit{\pageref{objects_s196}}
  
\texttt{fltan}, \textit{\pageref{objects_s194}}
  
\texttt{fltruncate}, \textit{\pageref{objects_s190}}
  
fluid binding, \pageref{control_s61}
  
\texttt{flush-output-port}, \textit{\pageref{io_s74}}
  
\texttt{flzero?}, \textit{\pageref{objects_s179}}
  
\texttt{fold-left}, \textit{\pageref{control_s38}}
  
\texttt{fold-right}, \textit{\pageref{control_s41}}
  
folding, \pageref{control_s39}, \pageref{control_s42}
  
\texttt{for-all}, \textit{\pageref{control_s37}}
  
\texttt{for-each}, \textit{\pageref{control_s33}}
  
\texttt{force}, \textit{\pageref{control_s65}}
  
formal parameters, \pageref{start_s62}, \pageref{start_s70}, \pageref{binding_s5}
  
formatted output, \pageref{examples_s37}
  
\texttt{fprintf}, \pageref{examples_s38}
  
free variable, \pageref{start_s68}
  
\texttt{free-identifier=?}, \textit{\pageref{syntax_s37}}
  
\texttt{frequency}, \pageref{examples_s24}
  
\texttt{fx*}, \textit{\pageref{objects_s159}}
  
\texttt{fx*/carry}, \textit{\pageref{objects_s162}}
  
\texttt{fx+}, \textit{\pageref{objects_s157}}
  
\texttt{fx+/carry}, \textit{\pageref{objects_s162}}
  
\texttt{fx-}, \textit{\pageref{objects_s158}}
  
\texttt{fx-/carry}, \textit{\pageref{objects_s162}}
  
\texttt{fx\textless{}=?}, \textit{\pageref{objects_s153}}
  
\texttt{fx\textless{}?}, \textit{\pageref{objects_s153}}
  
\texttt{fx=?}, \textit{\pageref{objects_s153}}
  
\texttt{fx\textgreater{}=?}, \textit{\pageref{objects_s153}}
  
\texttt{fx\textgreater{}?}, \textit{\pageref{objects_s153}}
  
\texttt{fxand}, \textit{\pageref{objects_s163}}
  
\texttt{fxarithmetic-shift}, \textit{\pageref{objects_s173}}
  
\texttt{fxarithmetic-shift-left}, \textit{\pageref{objects_s172}}
  
\texttt{fxarithmetic-shift-right}, \textit{\pageref{objects_s172}}
  
\texttt{fxbit-count}, \textit{\pageref{objects_s165}}
  
\texttt{fxbit-field}, \textit{\pageref{objects_s170}}
  
\texttt{fxbit-set?}, \textit{\pageref{objects_s168}}
  
\texttt{fxcopy-bit}, \textit{\pageref{objects_s169}}
  
\texttt{fxcopy-bit-field}, \textit{\pageref{objects_s171}}
  
\texttt{fxdiv}, \textit{\pageref{objects_s160}}
  
\texttt{fxdiv-and-mod}, \textit{\pageref{objects_s160}}
  
\texttt{fxdiv0}, \textit{\pageref{objects_s161}}
  
\texttt{fxdiv0-and-mod0}, \textit{\pageref{objects_s161}}
  
\texttt{fxeven?}, \textit{\pageref{objects_s155}}
  
\texttt{fxfirst-bit-set}, \textit{\pageref{objects_s167}}
  
\texttt{fxif}, \textit{\pageref{objects_s164}}
  
\texttt{fxior}, \textit{\pageref{objects_s163}}
  
\texttt{fxlength}, \textit{\pageref{objects_s166}}
  
\texttt{fxmax}, \textit{\pageref{objects_s156}}
  
\texttt{fxmin}, \textit{\pageref{objects_s156}}
  
\texttt{fxmod}, \textit{\pageref{objects_s160}}
  
\texttt{fxmod0}, \textit{\pageref{objects_s161}}
  
\texttt{fxnegative?}, \textit{\pageref{objects_s154}}
  
\texttt{fxnot}, \textit{\pageref{objects_s163}}
  
\texttt{fxodd?}, \textit{\pageref{objects_s155}}
  
\texttt{fxpositive?}, \textit{\pageref{objects_s154}}
  
\texttt{fxreverse-bit-field}, \textit{\pageref{objects_s175}}
  
\texttt{fxrotate-bit-field}, \textit{\pageref{objects_s174}}
  
\texttt{fxxor}, \textit{\pageref{objects_s163}}
  
\texttt{fxzero?}, \textit{\pageref{objects_s154}}
  
garbage collector, \pageref{intro_s3}
  
\texttt{gcd}, \textit{\pageref{objects_s109}}
  
\texttt{generate-temporaries}, \textit{\pageref{syntax_s49}}
  
generative, \pageref{records_s4}
  
\texttt{get-bytevector-all}, \textit{\pageref{io_s60}}
  
\texttt{get-bytevector-n}, \textit{\pageref{io_s57}}
  
\texttt{get-bytevector-n!}, \textit{\pageref{io_s58}}
  
\texttt{get-bytevector-some}, \textit{\pageref{io_s59}}
  
\texttt{get-char}, \textit{\pageref{io_s61}}
  
\texttt{get-datum}, \textit{\pageref{io_s67}}
  
\texttt{get-line}, \textit{\pageref{io_s66}}
  
\texttt{get-string-all}, \textit{\pageref{io_s65}}
  
\texttt{get-string-n}, \textit{\pageref{io_s63}}
  
\texttt{get-string-n!}, \textit{\pageref{io_s64}}
  
\texttt{get-u8}, \textit{\pageref{io_s55}}
  
\texttt{getq}, \pageref{start_s184}
  
\texttt{goodbye}, \pageref{start_s133}
  
\texttt{greatest-fixnum}, \textit{\pageref{objects_s151}}
  
\texttt{guard}, \textit{\pageref{exceptions_s8}}
  
hare and tortoise, \pageref{start_s202}, \pageref{further_s40}
  
\texttt{hashtable-clear!}, \textit{\pageref{objects_s287}}
  
\texttt{hashtable-contains?}, \textit{\pageref{objects_s282}}
  
\texttt{hashtable-copy}, \textit{\pageref{objects_s286}}
  
\texttt{hashtable-delete!}, \textit{\pageref{objects_s284}}
  
\texttt{hashtable-entries}, \textit{\pageref{objects_s289}}
  
\texttt{hashtable-equivalence-function}, \textit{\pageref{objects_s278}}
  
\texttt{hashtable-hash-function}, \textit{\pageref{objects_s278}}
  
\texttt{hashtable-keys}, \textit{\pageref{objects_s288}}
  
\texttt{hashtable-mutable?}, \textit{\pageref{objects_s277}}
  
\texttt{hashtable-ref}, \textit{\pageref{objects_s281}}
  
\texttt{hashtable-set!}, \textit{\pageref{objects_s280}}
  
\texttt{hashtable-size}, \textit{\pageref{objects_s285}}
  
\texttt{hashtable-update!}, \textit{\pageref{objects_s283}}
  
\texttt{hashtable?}, \textit{\pageref{objects_s25}}
  
hashtables, \pageref{objects_s272}
  
\texttt{i/o-decoding-error?}, \textit{\pageref{exceptions_s42}}
  
\texttt{i/o-encoding-error-char}, \textit{\pageref{exceptions_s43}}
  
\texttt{i/o-encoding-error?}, \textit{\pageref{exceptions_s43}}
  
\texttt{i/o-error-filename}, \textit{\pageref{exceptions_s36}}
  
\texttt{i/o-error-port}, \textit{\pageref{exceptions_s41}}
  
\texttt{i/o-error-position}, \textit{\pageref{exceptions_s35}}
  
\texttt{i/o-error?}, \textit{\pageref{exceptions_s32}}
  
\texttt{i/o-file-already-exists-error?}, \textit{\pageref{exceptions_s39}}
  
\texttt{i/o-file-does-not-exist-error?}, \textit{\pageref{exceptions_s40}}
  
\texttt{i/o-file-is-read-only-error?}, \textit{\pageref{exceptions_s38}}
  
\texttt{i/o-file-protection-error?}, \textit{\pageref{exceptions_s37}}
  
\texttt{i/o-filename-error?}, \textit{\pageref{exceptions_s36}}
  
\texttt{i/o-invalid-position-error?}, \textit{\pageref{exceptions_s35}}
  
\texttt{i/o-port-error?}, \textit{\pageref{exceptions_s41}}
  
\texttt{i/o-read-error?}, \textit{\pageref{exceptions_s33}}
  
\texttt{i/o-write-error?}, \textit{\pageref{exceptions_s34}}
  
\texttt{identifier-syntax}, \pageref{syntax_s9}, \textit{\pageref{syntax_s27}}, \pageref{syntax_s43}, \pageref{syntax_s62}, \pageref{syntax_s64}
  
\texttt{identifier?}, \textit{\pageref{syntax_s35}}
  
identifiers, \pageref{intro_s30}
  
\texttt{if}, \pageref{start_s99}, \pageref{start_s102}, \pageref{start_s125}, \pageref{start_s175}, \pageref{further_s7}, \textit{\pageref{control_s8}}
  
\texttt{imag-part}, \textit{\pageref{objects_s121}}
  
immutability of exports, \pageref{libraries_s16}
  
\texttt{immutable}, \textit{\pageref{records_s16}}
  
\texttt{implementation-restriction-violation?}, \textit{\pageref{exceptions_s28}}
  
implicit \texttt{begin}, \pageref{control_s7}
  
\texttt{import}, \pageref{libraries_s4}
  
import level, \pageref{libraries_s6}
  
import spec, \pageref{libraries_s5}, \pageref{libraries_s8}
  
improper list, \pageref{start_s29}, \pageref{objects_s32}
  
\texttt{include}, \pageref{syntax_s48}
  
indirect exports, \pageref{libraries_s15}
  
\texttt{inexact}, \textit{\pageref{objects_s112}}
  
\texttt{inexact-\textgreater{}exact}, \textit{\pageref{objects_s116}}
  
\texttt{inexact?}, \pageref{objects_s74}, \textit{\pageref{objects_s87}}
  
\texttt{infinite?}, \textit{\pageref{objects_s97}}
  
inheritance, \pageref{examples_s67}
  
inheritance in records, \pageref{records_s8}
  
input port, \pageref{io_s1}
  
\texttt{input-port?}, \textit{\pageref{io_s44}}
  
\texttt{integer-\textgreater{}char}, \textit{\pageref{objects_s211}}
  
\texttt{integer-divide}, \pageref{further_s73}
  
\texttt{integer-valued?}, \textit{\pageref{objects_s18}}
  
\texttt{integer?}, \textit{\pageref{objects_s17}}, \pageref{objects_s68}
  
integers, \pageref{objects_s64}
  
integrable procedures, \pageref{syntax_s60}
  
internal definitions, \pageref{further_s81}, \pageref{binding_s6}
  
internal state, \pageref{start_s167}
  
\texttt{interpret}, \pageref{examples_s46}
  
interpreter, \pageref{intro_s8}, \pageref{examples_s48}
  
intraline whitespace, \pageref{grammar_s4}
  
\texttt{irritants-condition?}, \textit{\pageref{exceptions_s25}}
  
iteration, \pageref{intro_s21}, \pageref{start_s145}, \pageref{further_s43}, \pageref{control_s22}, \pageref{control_s26}, \pageref{control_s32}, \pageref{control_s35}, \pageref{control_s40}, \pageref{control_s43}, \pageref{control_s49}
  
keywords, \pageref{intro_s11}, \pageref{further_s15}, \pageref{syntax_s11}
  
\texttt{l} (long), \pageref{objects_s85}
  
\texttt{lambda}, \pageref{start_s60}, \pageref{start_s71}, \pageref{further_s6}, \textit{\pageref{binding_s3}}, \pageref{binding_s9}
  
\texttt{lambda*}, \pageref{binding_s12}
  
latin-1, \pageref{io_s11}
  
\texttt{latin-1-codec}, \textit{\pageref{io_s22}}
  
\texttt{lazy}, \pageref{start_s172}
  
lazy evaluation, \pageref{start_s171}, \pageref{control_s64}
  
\texttt{lcm}, \textit{\pageref{objects_s110}}
  
\texttt{least-fixnum}, \textit{\pageref{objects_s151}}
  
\texttt{length}, \pageref{start_s136}, \textit{\pageref{objects_s46}}
  
\texttt{let}, \pageref{start_s51}, \pageref{start_s69}, \pageref{further_s33}, \textit{\pageref{binding_s16}}, \textit{\pageref{control_s20}}
  
\texttt{let*}, \pageref{further_s28}, \textit{\pageref{binding_s18}}
  
\texttt{let*-values}, \textit{\pageref{binding_s23}}, \pageref{control_s79}
  
\texttt{let}-bound variables, \pageref{start_s53}
  
\texttt{let-syntax}, \pageref{syntax_s4}, \textit{\pageref{syntax_s13}}, \pageref{syntax_s57}
  
\texttt{let-values}, \textit{\pageref{binding_s23}}, \pageref{control_s78}, \pageref{syntax_s51}
  
\texttt{letrec}, \pageref{further_s35}, \pageref{further_s84}, \textit{\pageref{binding_s20}}, \pageref{syntax_s50}
  
\texttt{letrec*}, \textit{\pageref{binding_s22}}
  
\texttt{letrec-syntax}, \pageref{syntax_s5}, \textit{\pageref{syntax_s13}}, \pageref{syntax_s56}
  
lexical scoping, \pageref{intro_s12}, \pageref{intro_s17}, \pageref{start_s56}, \pageref{further_s24}
  
\texttt{lexical-violation?}, \textit{\pageref{exceptions_s29}}
  
libraries, \pageref{libraries_s0}
  
library body, \pageref{libraries_s14}
  
library version, \pageref{libraries_s2}
  
library version reference, \pageref{libraries_s13}
  
light-weight threads, \pageref{examples_s85}
  
line buffering, \pageref{io_s18}
  
line ending, \pageref{grammar_s3}
  
Lisp, \pageref{preface_s0}, \pageref{intro_s26}
  
\texttt{lisp-cdr}, \pageref{start_s115}
  
\texttt{list}, \pageref{start_s33}, \pageref{start_s82}, \pageref{start_s86}, \textit{\pageref{objects_s43}}
  
list constants, \pageref{intro_s31}
  
list syntax, \pageref{grammar_s19}
  
\texttt{list-\textgreater{}string}, \textit{\pageref{objects_s229}}
  
\texttt{list-\textgreater{}vector}, \textit{\pageref{objects_s238}}
  
\texttt{list-copy}, \pageref{start_s140}
  
\texttt{list-ref}, \textit{\pageref{objects_s47}}
  
\texttt{list-sort}, \textit{\pageref{objects_s62}}, \pageref{examples_s9}
  
\texttt{list-tail}, \textit{\pageref{objects_s48}}
  
\texttt{list?}, \pageref{start_s200}, \pageref{further_s39}, \pageref{further_s42}, \pageref{further_s85}, \textit{\pageref{objects_s45}}
  
lists, \pageref{start_s13}, \pageref{start_s20}, \pageref{objects_s28}
  
literals, \pageref{syntax_s15}
  
\texttt{load}, \pageref{start_s0}
  
local variable bindings, \pageref{binding_s17}
  
\texttt{log}, \textit{\pageref{objects_s130}}
  
\texttt{lookahead-char}, \textit{\pageref{io_s62}}
  
\texttt{lookahead-u8}, \textit{\pageref{io_s56}}
  
\texttt{loop}, \pageref{syntax_s46}
  
looping, \pageref{intro_s22}
  
macros, \pageref{syntax_s2}
  
\texttt{magnitude}, \pageref{objects_s106}, \textit{\pageref{objects_s125}}
  
\texttt{make-assertion-violation}, \textit{\pageref{exceptions_s21}}
  
\texttt{make-bytevector}, \textit{\pageref{objects_s242}}
  
\texttt{make-counter}, \pageref{start_s168}, \pageref{start_s187}
  
\texttt{make-custom-binary-input-port}, \textit{\pageref{io_s41}}
  
\texttt{make-custom-binary-input/output-port}, \textit{\pageref{io_s41}}
  
\texttt{make-custom-binary-output-port}, \textit{\pageref{io_s41}}
  
\texttt{make-custom-textual-input-port}, \textit{\pageref{io_s42}}
  
\texttt{make-custom-textual-input/output-port}, \textit{\pageref{io_s42}}
  
\texttt{make-custom-textual-output-port}, \textit{\pageref{io_s42}}
  
\texttt{make-enumeration}, \textit{\pageref{objects_s291}}
  
\texttt{make-eq-hashtable}, \textit{\pageref{objects_s274}}
  
\texttt{make-eqv-hashtable}, \textit{\pageref{objects_s275}}
  
\texttt{make-error}, \textit{\pageref{exceptions_s22}}
  
\texttt{make-hashtable}, \textit{\pageref{objects_s276}}
  
\texttt{make-i/o-decoding-error}, \textit{\pageref{exceptions_s42}}
  
\texttt{make-i/o-encoding-error}, \textit{\pageref{exceptions_s43}}
  
\texttt{make-i/o-error}, \textit{\pageref{exceptions_s32}}
  
\texttt{make-i/o-file-already-exists-error}, \textit{\pageref{exceptions_s39}}
  
\texttt{make-i/o-file-does-not-exist-error}, \textit{\pageref{exceptions_s40}}
  
\texttt{make-i/o-file-is-read-only-error}, \textit{\pageref{exceptions_s38}}
  
\texttt{make-i/o-file-protection-error}, \textit{\pageref{exceptions_s37}}
  
\texttt{make-i/o-filename-error}, \textit{\pageref{exceptions_s36}}
  
\texttt{make-i/o-invalid-position-error}, \textit{\pageref{exceptions_s35}}
  
\texttt{make-i/o-port-error}, \textit{\pageref{exceptions_s41}}
  
\texttt{make-i/o-read-error}, \textit{\pageref{exceptions_s33}}
  
\texttt{make-i/o-write-error}, \textit{\pageref{exceptions_s34}}
  
\texttt{make-implementation-restriction-violation}, \textit{\pageref{exceptions_s28}}
  
\texttt{make-irritants-condition}, \textit{\pageref{exceptions_s25}}
  
\texttt{make-lexical-violation}, \textit{\pageref{exceptions_s29}}
  
\texttt{make-list}, \pageref{start_s153}, \pageref{binding_s14}
  
\texttt{make-message-condition}, \textit{\pageref{exceptions_s24}}
  
\texttt{make-no-infinities-violation}, \textit{\pageref{exceptions_s44}}
  
\texttt{make-no-nans-violation}, \textit{\pageref{exceptions_s45}}
  
\texttt{make-non-continuable-violation}, \textit{\pageref{exceptions_s27}}
  
\texttt{make-polar}, \textit{\pageref{objects_s123}}
  
\texttt{make-promise}, \pageref{control_s67}
  
\texttt{make-queue}, \pageref{start_s182}
  
\texttt{make-record-constructor-descriptor}, \textit{\pageref{records_s24}}
  
\texttt{make-record-type-descriptor}, \pageref{records_s2}, \textit{\pageref{records_s20}}
  
make-record-type-descriptor, \pageref{records_s19}
  
\texttt{make-rectangular}, \textit{\pageref{objects_s122}}
  
\texttt{make-serious-condition}, \textit{\pageref{exceptions_s19}}
  
\texttt{make-stack}, \pageref{start_s178}, \pageref{start_s190}
  
\texttt{make-string}, \textit{\pageref{objects_s218}}
  
\texttt{make-syntax-violation}, \textit{\pageref{exceptions_s30}}
  
\texttt{make-transcoder}, \textit{\pageref{io_s19}}
  
\texttt{make-undefined-violation}, \textit{\pageref{exceptions_s31}}
  
\texttt{make-variable-transformer}, \pageref{syntax_s10}, \pageref{syntax_s28}, \textit{\pageref{syntax_s42}}
  
\texttt{make-vector}, \textit{\pageref{objects_s232}}
  
\texttt{make-violation}, \textit{\pageref{exceptions_s20}}
  
\texttt{make-warning}, \textit{\pageref{exceptions_s23}}
  
\texttt{make-who-condition}, \textit{\pageref{exceptions_s26}}
  
\texttt{map}, \pageref{start_s147}, \pageref{start_s162}, \textit{\pageref{control_s30}}, \pageref{examples_s21}
  
\texttt{map1}, \pageref{start_s148}
  
mapping, \pageref{start_s146}, \pageref{control_s31}, \pageref{control_s34}, \pageref{control_s45}, \pageref{control_s48}
  
matrix multiplication, \pageref{examples_s1}
  
\texttt{max}, \textit{\pageref{objects_s107}}
  
\texttt{member}, \textit{\pageref{objects_s51}}
  
\texttt{memp}, \textit{\pageref{objects_s52}}
  
\texttt{memq}, \textit{\pageref{objects_s51}}
  
\texttt{memv}, \pageref{start_s141}, \textit{\pageref{objects_s51}}
  
\texttt{merge}, \pageref{examples_s11}
  
\texttt{message-condition?}, \textit{\pageref{exceptions_s24}}
  
messages, \pageref{start_s177}, \pageref{examples_s62}
  
meta-circular interpreter, \pageref{examples_s47}
  
\texttt{method}, \pageref{syntax_s67}
  
\texttt{min}, \textit{\pageref{objects_s108}}
  
\texttt{mod}, \textit{\pageref{objects_s99}}
  
\texttt{mod0}, \textit{\pageref{objects_s100}}
  
\texttt{modulo}, \textit{\pageref{objects_s98}}
  
\texttt{mul}, \pageref{examples_s2}
  
multiple values, \pageref{intro_s54}
  
multiprocessing, \pageref{examples_s84}
  
\texttt{mutable}, \textit{\pageref{records_s16}}
  
mutually recursive procedures, \pageref{further_s36}, \pageref{binding_s21}
  
named \texttt{let}, \pageref{further_s41}, \pageref{further_s50}, \pageref{control_s21}
  
naming conventions, \pageref{intro_s45}
  
\texttt{nan?}, \textit{\pageref{objects_s97}}
  
\texttt{native-endianness}, \textit{\pageref{objects_s241}}
  
\texttt{native-eol-style}, \textit{\pageref{io_s24}}
  
\texttt{native-transcoder}, \textit{\pageref{io_s21}}
  
\texttt{negative?}, \textit{\pageref{objects_s95}}
  
nested engines, \pageref{examples_s109}
  
nested \texttt{let} expressions, \pageref{binding_s19}
  
\texttt{newline}, \textit{\pageref{io_s87}}
  
\texttt{no-infinities-violation?}, \textit{\pageref{exceptions_s44}}
  
\texttt{no-nans-violation?}, \textit{\pageref{exceptions_s45}}
  
\texttt{non-continuable-violation?}, \textit{\pageref{exceptions_s27}}
  
nondeterministic computations, \pageref{examples_s87}, \pageref{examples_s95}
  
\texttt{nongenerative}, \textit{\pageref{records_s16}}
  
nongenerative, \pageref{records_s5}
  
nonlocal exits, \pageref{control_s55}, \pageref{control_s60}
  
\texttt{not}, \pageref{start_s100}, \textit{\pageref{control_s10}}
  
\texttt{null-environment}, \textit{\pageref{control_s82}}
  
\texttt{null?}, \pageref{start_s113}, \textit{\pageref{objects_s15}}
  
number syntax, \pageref{grammar_s18}
  
\texttt{number-\textgreater{}string}, \textit{\pageref{objects_s148}}
  
\texttt{number?}, \pageref{start_s120}, \textit{\pageref{objects_s17}}
  
numbers, \pageref{start_s5}, \pageref{objects_s63}
  
\texttt{numerator}, \textit{\pageref{objects_s118}}
  
object identity, \pageref{objects_s11}
  
\texttt{object-\textgreater{}string}, \pageref{io_s40}
  
object-oriented programming, \pageref{syntax_s66}, \pageref{examples_s61}
  
objects, \pageref{intro_s1}
  
occur free, \pageref{start_s67}, \pageref{start_s75}
  
octet, \pageref{io_s8}
  
\texttt{odd?}, \pageref{start_s159}, \pageref{further_s38}, \pageref{further_s83}, \textit{\pageref{objects_s96}}
  
\texttt{only} import set, \pageref{libraries_s9}
  
\texttt{opaque}, \textit{\pageref{records_s16}}
  
opaque record type, \pageref{records_s15}, \pageref{records_s33}
  
\texttt{open-bytevector-input-port}, \textit{\pageref{io_s34}}
  
\texttt{open-bytevector-output-port}, \textit{\pageref{io_s36}}
  
\texttt{open-file-input-port}, \textit{\pageref{io_s29}}
  
\texttt{open-file-input/output-port}, \textit{\pageref{io_s31}}
  
\texttt{open-file-output-port}, \textit{\pageref{io_s30}}
  
\texttt{open-input-file}, \textit{\pageref{io_s75}}
  
\texttt{open-output-file}, \textit{\pageref{io_s76}}
  
\texttt{open-string-input-port}, \textit{\pageref{io_s35}}
  
\texttt{open-string-output-port}, \textit{\pageref{io_s37}}
  
operating system, \pageref{examples_s94}, \pageref{examples_s106}
  
operations on objects, \pageref{objects_s0}
  
operator precedence, \pageref{start_s12}
  
optional arguments, \pageref{binding_s10}
  
\texttt{or}, \pageref{start_s101}, \pageref{further_s23}, \textit{\pageref{control_s12}}
  
order of evaluation, \pageref{start_s48}, \pageref{control_s2}
  
output port, \pageref{io_s2}
  
\texttt{output-port-buffer-mode}, \textit{\pageref{io_s52}}
  
\texttt{output-port?}, \textit{\pageref{io_s44}}
  
\texttt{pair?}, \pageref{start_s118}, \textit{\pageref{objects_s16}}
  
pairs, \pageref{start_s27}, \pageref{objects_s26}
  
\texttt{parent}, \textit{\pageref{records_s16}}
  
parent type, \pageref{records_s9}
  
\texttt{parent-rtd}, \textit{\pageref{records_s16}}
  
\texttt{partition}, \textit{\pageref{objects_s56}}
  
pattern variable, \pageref{syntax_s17}
  
pattern variables, \pageref{further_s19}, \pageref{syntax_s32}
  
patterns, \pageref{syntax_s16}
  
\texttt{peek-char}, \textit{\pageref{io_s83}}
  
Petite Chez Scheme, \pageref{preface_s4}
  
pointers, \pageref{intro_s5}
  
\texttt{por} (parallel-or), \pageref{examples_s96}
  
port, \pageref{io_s0}
  
\texttt{port-eof?}, \textit{\pageref{io_s68}}
  
\texttt{port-has-port-position?}, \textit{\pageref{io_s49}}
  
\texttt{port-has-set-port-position!?}, \textit{\pageref{io_s50}}
  
\texttt{port-position}, \textit{\pageref{io_s49}}
  
\texttt{port-transcoder}, \textit{\pageref{io_s48}}
  
\texttt{port?}, \textit{\pageref{io_s43}}
  
\texttt{positive?}, \textit{\pageref{objects_s94}}
  
predicates, \pageref{intro_s48}, \pageref{start_s110}, \pageref{objects_s6}
  
\texttt{prefix} import set, \pageref{libraries_s11}
  
prefix notation, \pageref{start_s3}, \pageref{start_s11}
  
primitive procedures, \pageref{intro_s7}
  
\texttt{printf}, \pageref{examples_s39}
  
procedure application, \pageref{start_s10}, \pageref{start_s14}, \pageref{start_s43}, \pageref{start_s63}, \textit{\pageref{control_s1}}
  
procedure definition, \pageref{intro_s16}, \pageref{start_s80}, \pageref{binding_s25}
  
\texttt{procedure?}, \textit{\pageref{objects_s23}}
  
procedures, \pageref{start_s61}, \pageref{binding_s1}, \pageref{binding_s4}
  
\texttt{product}, \pageref{further_s63}, \pageref{further_s74}
  
proper list, \pageref{start_s28}, \pageref{start_s201}, \pageref{objects_s31}
  
\texttt{protocol}, \textit{\pageref{records_s16}}
  
protocol for records, \pageref{records_s11}, \pageref{records_s27}
  
\texttt{put-bytevector}, \textit{\pageref{io_s70}}
  
\texttt{put-char}, \textit{\pageref{io_s71}}
  
\texttt{put-datum}, \textit{\pageref{io_s73}}, \pageref{examples_s31}
  
\texttt{put-string}, \textit{\pageref{io_s72}}
  
\texttt{put-u8}, \textit{\pageref{io_s69}}
  
\texttt{putq!}, \pageref{start_s183}
  
\texttt{quadratic-formula}, \pageref{start_s166}
  
\texttt{quasiquote} ( \texttt{`} ), \textit{\pageref{objects_s5}}
  
\texttt{quasisyntax} ( \texttt{\#{}`} ), \textit{\pageref{syntax_s40}}
  
question mark ( \texttt{?} ), \pageref{intro_s47}, \pageref{start_s112}
  
queue, \pageref{start_s180}
  
\texttt{quote} ( \texttt{'} ), \pageref{start_s16}, \pageref{start_s45}, \pageref{further_s5}, \textit{\pageref{objects_s2}}
  
\texttt{quotient}, \textit{\pageref{objects_s98}}
  
\texttt{raise}, \textit{\pageref{exceptions_s3}}
  
\texttt{raise-continuable}, \textit{\pageref{exceptions_s3}}
  
rational numbers, \pageref{objects_s65}
  
\texttt{rational-valued?}, \textit{\pageref{objects_s18}}
  
\texttt{rational?}, \textit{\pageref{objects_s17}}, \pageref{objects_s69}
  
\texttt{rationalize}, \textit{\pageref{objects_s117}}
  
rcd, \pageref{records_s26}
  
\texttt{read}, \textit{\pageref{io_s81}}
  
\texttt{read-char}, \textit{\pageref{io_s82}}
  
real numbers, \pageref{objects_s66}
  
\texttt{real-\textgreater{}flonum}, \textit{\pageref{objects_s198}}
  
\texttt{real-part}, \textit{\pageref{objects_s120}}
  
\texttt{real-valued?}, \textit{\pageref{objects_s18}}
  
\texttt{real?}, \textit{\pageref{objects_s17}}, \pageref{objects_s70}
  
\texttt{rec}, \pageref{syntax_s52}
  
\texttt{reciprocal}, \pageref{start_s4}, \pageref{start_s109}, \pageref{start_s123}, \pageref{further_s76}
  
record generativity, \pageref{records_s3}
  
record inheritance, \pageref{records_s7}
  
record uid, \pageref{records_s6}
  
\texttt{record-accessor}, \textit{\pageref{records_s31}}
  
\texttt{record-constructor}, \textit{\pageref{records_s29}}
  
record-constructor descriptor, \pageref{records_s25}
  
\texttt{record-constructor-descriptor}, \textit{\pageref{records_s28}}
  
\texttt{record-field-mutable?}, \textit{\pageref{records_s39}}
  
\texttt{record-mutator}, \textit{\pageref{records_s32}}
  
\texttt{record-predicate}, \textit{\pageref{records_s30}}
  
\texttt{record-rtd}, \textit{\pageref{records_s41}}
  
record-type descriptor, \pageref{records_s17}
  
\texttt{record-type-descriptor}, \textit{\pageref{records_s28}}
  
\texttt{record-type-descriptor?}, \textit{\pageref{records_s23}}
  
\texttt{record-type-field-names}, \textit{\pageref{records_s38}}
  
\texttt{record-type-generative?}, \textit{\pageref{records_s37}}
  
\texttt{record-type-name}, \textit{\pageref{records_s34}}
  
\texttt{record-type-opaque?}, \textit{\pageref{records_s37}}
  
\texttt{record-type-parent}, \textit{\pageref{records_s35}}
  
\texttt{record-type-sealed?}, \textit{\pageref{records_s37}}
  
\texttt{record-type-uid}, \textit{\pageref{records_s36}}
  
\texttt{record?}, \textit{\pageref{records_s40}}
  
records, \pageref{records_s0}
  
recursion, \pageref{intro_s19}, \pageref{start_s130}, \pageref{further_s32}, \pageref{control_s23}
  
recursion step, \pageref{start_s135}
  
recursive procedure, \pageref{start_s132}
  
\texttt{remainder}, \textit{\pageref{objects_s98}}
  
\texttt{remove}, \textit{\pageref{objects_s53}}
  
\texttt{remp}, \textit{\pageref{objects_s54}}
  
\texttt{remq}, \textit{\pageref{objects_s53}}
  
\texttt{remv}, \pageref{start_s143}, \textit{\pageref{objects_s53}}
  
\texttt{rename} import set, \pageref{libraries_s12}
  
\texttt{retry}, \pageref{further_s65}, \pageref{further_s78}
  
\texttt{reverse}, \textit{\pageref{objects_s50}}
  
Revised Reports, \pageref{preface_s2}, \pageref{intro_s0}
  
\texttt{round}, \textit{\pageref{objects_s104}}
  
\texttt{round-robin}, \pageref{examples_s93}
  
rtd, \pageref{records_s18}
  
\texttt{s} (short), \pageref{objects_s82}
  
Scheme standard, \pageref{preface_s1}
  
\texttt{scheme-report-environment}, \textit{\pageref{control_s82}}
  
scope, \pageref{start_s55}
  
\texttt{sealed}, \textit{\pageref{records_s16}}
  
sealed record type, \pageref{records_s14}
  
\texttt{segment-length}, \pageref{control_s73}
  
\texttt{segment-slope}, \pageref{control_s74}
  
semicolon ( \texttt{;} ), \pageref{intro_s44}, \pageref{grammar_s7}
  
\texttt{sequence}, \pageref{syntax_s55}
  
sequencing, \pageref{control_s5}
  
\texttt{serious-condition?}, \textit{\pageref{exceptions_s19}}
  
\texttt{set!}, \pageref{start_s165}, \pageref{further_s8}, \textit{\pageref{binding_s28}}
  
\texttt{set-car!}, \textit{\pageref{objects_s40}}
  
\texttt{set-cdr!}, \pageref{start_s197}, \textit{\pageref{objects_s41}}
  
\texttt{set-of}, \pageref{examples_s15}
  
\texttt{set-port-position!}, \textit{\pageref{io_s50}}
  
sets, \pageref{examples_s16}
  
shadowing, \pageref{intro_s15}, \pageref{start_s54}, \pageref{start_s81}
  
\texttt{shhh}, \pageref{start_s169}
  
\texttt{shorter}, \pageref{start_s129}, \pageref{start_s156}
  
\texttt{shorter?}, \pageref{start_s157}
  
side effects, \pageref{intro_s52}, \pageref{control_s6}
  
simple condition, \pageref{exceptions_s12}
  
\texttt{simple-conditions}, \textit{\pageref{exceptions_s16}}
  
\texttt{sin}, \textit{\pageref{objects_s131}}
  
\texttt{sint-list-\textgreater{}bytevector}, \textit{\pageref{objects_s261}}
  
\texttt{sort}, \pageref{examples_s10}
  
\texttt{split}, \pageref{control_s76}
  
\texttt{sqrt}, \textit{\pageref{objects_s127}}
  
\texttt{square}, \pageref{start_s2}
  
stack objects, \pageref{start_s176}
  
\texttt{standard-error-port}, \textit{\pageref{io_s33}}
  
\texttt{standard-input-port}, \textit{\pageref{io_s33}}
  
\texttt{standard-output-port}, \textit{\pageref{io_s33}}
  
streams, \pageref{control_s66}
  
\texttt{string}, \textit{\pageref{objects_s217}}
  
string syntax, \pageref{grammar_s16}
  
\texttt{string-\textgreater{}bytevector}, \textit{\pageref{io_s92}}
  
\texttt{string-\textgreater{}list}, \textit{\pageref{objects_s228}}
  
\texttt{string-\textgreater{}number}, \textit{\pageref{objects_s147}}
  
\texttt{string-\textgreater{}symbol}, \textit{\pageref{objects_s269}}
  
\texttt{string-\textgreater{}utf16}, \textit{\pageref{io_s94}}
  
\texttt{string-\textgreater{}utf32}, \textit{\pageref{io_s94}}
  
\texttt{string-\textgreater{}utf8}, \textit{\pageref{io_s93}}
  
\texttt{string-append}, \textit{\pageref{objects_s223}}
  
\texttt{string-ci-hash}, \textit{\pageref{objects_s279}}
  
\texttt{string-ci\textless{}=?}, \textit{\pageref{objects_s216}}
  
\texttt{string-ci\textless{}?}, \textit{\pageref{objects_s216}}
  
\texttt{string-ci=?}, \textit{\pageref{objects_s216}}
  
\texttt{string-ci\textgreater{}=?}, \textit{\pageref{objects_s216}}
  
\texttt{string-ci\textgreater{}?}, \textit{\pageref{objects_s216}}
  
\texttt{string-copy}, \textit{\pageref{objects_s222}}
  
\texttt{string-downcase}, \textit{\pageref{objects_s226}}
  
\texttt{string-fill!}, \textit{\pageref{objects_s225}}
  
\texttt{string-foldcase}, \textit{\pageref{objects_s226}}
  
\texttt{string-for-each}, \textit{\pageref{control_s50}}
  
\texttt{string-hash}, \textit{\pageref{objects_s279}}
  
\texttt{string-length}, \textit{\pageref{objects_s219}}
  
\texttt{string-normalize-nfc}, \textit{\pageref{objects_s227}}
  
\texttt{string-normalize-nfd}, \textit{\pageref{objects_s227}}
  
\texttt{string-normalize-nfkc}, \textit{\pageref{objects_s227}}
  
\texttt{string-normalize-nfkd}, \textit{\pageref{objects_s227}}
  
\texttt{string-ref}, \textit{\pageref{objects_s220}}
  
\texttt{string-set!}, \textit{\pageref{objects_s221}}
  
\texttt{string-titlecase}, \textit{\pageref{objects_s226}}
  
\texttt{string-upcase}, \textit{\pageref{objects_s226}}
  
\texttt{string\textless{}=?}, \textit{\pageref{objects_s215}}
  
\texttt{string\textless{}?}, \textit{\pageref{objects_s215}}
  
\texttt{string=?}, \textit{\pageref{objects_s215}}
  
\texttt{string\textgreater{}=?}, \textit{\pageref{objects_s215}}
  
\texttt{string\textgreater{}?}, \textit{\pageref{objects_s215}}
  
\texttt{string?}, \pageref{start_s121}, \textit{\pageref{objects_s20}}
  
strings, \pageref{start_s1}, \pageref{objects_s212}
  
structured forms, \pageref{intro_s29}
  
structures, \pageref{syntax_s69}
  
\texttt{substring}, \pageref{binding_s15}, \textit{\pageref{objects_s224}}
  
sum, \pageref{further_s34}
  
symbol syntax, \pageref{grammar_s17}
  
symbol table, \pageref{objects_s267}
  
\texttt{symbol-\textgreater{}string}, \textit{\pageref{objects_s270}}
  
\texttt{symbol-hash}, \textit{\pageref{objects_s279}}
  
\texttt{symbol=?}, \textit{\pageref{objects_s268}}
  
\texttt{symbol?}, \pageref{start_s119}, \textit{\pageref{objects_s22}}
  
symbols, \pageref{start_s19}, \pageref{objects_s266}
  
syntactic extensions, \pageref{intro_s25}, \pageref{start_s46}, \pageref{further_s2}, \pageref{further_s12}, \pageref{syntax_s0}
  
syntactic forms, \pageref{start_s17}, \pageref{further_s1}, \pageref{syntax_s1}
  
\texttt{syntax}, \pageref{syntax_s8}
  
\texttt{syntax} ( \texttt{\#{}'} ), \textit{\pageref{syntax_s33}}
  
syntax object, \pageref{syntax_s29}
  
syntax violation, \pageref{intro_s56}
  
\texttt{syntax-\textgreater{}datum}, \textit{\pageref{syntax_s44}}
  
\texttt{syntax-case}, \pageref{syntax_s7}, \textit{\pageref{syntax_s30}}
  
\texttt{syntax-rules}, \pageref{syntax_s6}, \textit{\pageref{syntax_s14}}, \pageref{syntax_s34}, \pageref{examples_s18}
  
\texttt{syntax-violation}, \textit{\pageref{exceptions_s6}}
  
\texttt{syntax-violation-form}, \textit{\pageref{exceptions_s30}}
  
\texttt{syntax-violation-subform}, \textit{\pageref{exceptions_s30}}
  
\texttt{syntax-violation?}, \textit{\pageref{exceptions_s30}}
  
tail call, \pageref{intro_s23}, \pageref{further_s44}
  
tail recursion, \pageref{intro_s20}, \pageref{further_s45}
  
\texttt{tan}, \textit{\pageref{objects_s131}}
  
tconc, \pageref{start_s181}
  
\texttt{tell}, \pageref{start_s170}
  
templates, \pageref{syntax_s23}
  
textual port, \pageref{io_s7}
  
\texttt{textual-port?}, \textit{\pageref{io_s45}}
  
threads, \pageref{examples_s86}
  
thunk, \pageref{start_s173}, \pageref{control_s58}
  
\textit{ticks}, \textit{see} engines
  
timed preemption, \pageref{examples_s83}
  
timer interrupts, \pageref{examples_s97}
  
tokens, \pageref{grammar_s1}
  
top-level definitions, \pageref{start_s76}, \pageref{binding_s27}
  
top-level programs, \pageref{libraries_s1}
  
\texttt{trace}, \pageref{start_s138}
  
tracing, \pageref{start_s137}
  
\texttt{transcoded-port}, \textit{\pageref{io_s47}}
  
transcoder, \pageref{io_s9}
  
\texttt{transcoder-codec}, \textit{\pageref{io_s20}}
  
\texttt{transcoder-eol-style}, \textit{\pageref{io_s20}}
  
\texttt{transcoder-error-handling-mode}, \textit{\pageref{io_s20}}
  
transformer, \pageref{further_s14}
  
\texttt{tree-copy}, \pageref{start_s144}
  
true, \pageref{intro_s36}, \pageref{start_s106}
  
\texttt{truncate}, \textit{\pageref{objects_s101}}
  
type predicates, \pageref{start_s117}
  
\texttt{u8-list-\textgreater{}bytevector}, \textit{\pageref{objects_s253}}
  
\texttt{uint-list-\textgreater{}bytevector}, \textit{\pageref{objects_s261}}
  
\texttt{undefined-violation?}, \textit{\pageref{exceptions_s31}}
  
underscore ( \texttt{\_{}} ), \pageref{further_s17}, \pageref{syntax_s24}, \pageref{syntax_s58}
  
underscore (\texttt{\_{}}), \pageref{syntax_s19}
  
unification, \pageref{examples_s76}
  
\texttt{unify}, \pageref{examples_s78}
  
\texttt{unless}, \pageref{further_s31}, \textit{\pageref{control_s17}}
  
\texttt{unquote} ( \texttt{,} ), \textit{\pageref{objects_s5}}
  
\texttt{unquote-splicing} ( \texttt{,\@{}} ), \textit{\pageref{objects_s5}}
  
unspecified, \pageref{intro_s53}
  
\texttt{unsyntax} ( \texttt{\#{},} ), \textit{\pageref{syntax_s40}}
  
\texttt{unsyntax-splicing} ( \texttt{\#{},\@{}} ), \textit{\pageref{syntax_s40}}
  
unwind-protect (in Lisp), \pageref{control_s59}
  
utf-16, \pageref{io_s13}
  
\texttt{utf-16-codec}, \textit{\pageref{io_s22}}
  
utf-8, \pageref{io_s12}
  
\texttt{utf-8-codec}, \textit{\pageref{io_s22}}
  
\texttt{utf16-\textgreater{}string}, \textit{\pageref{io_s96}}
  
\texttt{utf32-\textgreater{}string}, \textit{\pageref{io_s96}}
  
\texttt{utf8-\textgreater{}string}, \textit{\pageref{io_s95}}
  
\texttt{values}, \pageref{control_s68}, \textit{\pageref{control_s70}}
  
variable binding, \pageref{start_s52}, \pageref{binding_s0}
  
variable reference, \textit{\pageref{binding_s2}}
  
variables, \pageref{intro_s10}, \pageref{start_s18}, \pageref{start_s50}, \pageref{start_s77}, \pageref{start_s164}
  
\texttt{vector}, \textit{\pageref{objects_s231}}
  
vector syntax, \pageref{grammar_s22}
  
\texttt{vector-\textgreater{}list}, \textit{\pageref{objects_s237}}
  
\texttt{vector-fill!}, \textit{\pageref{objects_s236}}
  
\texttt{vector-for-each}, \textit{\pageref{control_s47}}
  
\texttt{vector-length}, \textit{\pageref{objects_s233}}
  
\texttt{vector-map}, \textit{\pageref{control_s44}}
  
\texttt{vector-ref}, \textit{\pageref{objects_s234}}
  
\texttt{vector-set!}, \textit{\pageref{objects_s235}}
  
\texttt{vector-sort}, \textit{\pageref{objects_s239}}
  
\texttt{vector-sort!}, \textit{\pageref{objects_s239}}
  
\texttt{vector?}, \textit{\pageref{objects_s21}}
  
vectors, \pageref{start_s193}, \pageref{objects_s230}, \pageref{examples_s3}
  
\texttt{violation?}, \textit{\pageref{exceptions_s20}}
  
\texttt{warning?}, \textit{\pageref{exceptions_s23}}
  
\texttt{when}, \pageref{further_s30}, \textit{\pageref{control_s17}}
  
whitespace, \pageref{grammar_s2}
  
whitespace characters, \pageref{intro_s41}
  
\texttt{who-condition?}, \textit{\pageref{exceptions_s26}}
  
winders, \textit{see} \texttt{dynamic-wind}
  
\texttt{with-exception-handler}, \textit{\pageref{exceptions_s7}}
  
\texttt{with-input-from-file}, \textit{\pageref{io_s79}}
  
\texttt{with-output-to-file}, \textit{\pageref{io_s80}}
  
\texttt{with-syntax}, \textit{\pageref{syntax_s38}}
  
\texttt{write}, \textit{\pageref{io_s84}}, \pageref{examples_s32}
  
\texttt{write-char}, \textit{\pageref{io_s86}}
  
\texttt{x++}, \pageref{syntax_s63}
  
\texttt{zero?}, \textit{\pageref{objects_s93}}
\end{multicols}
}